---
title: "Ordering DIA Assay Libraries"
author: "Elizabeth Mojica"
date: "5/8/2022"
output: html_document
---

The purpose of this Rmd file is to order all of the modified peptide sequences from the Skyline outputs from each tissue/digestion/experiment to match the order of the DIA assay library that I used to create the histone PTM quantification excel files. Once all of the files have a matching order of modified peptide sequence, then their values of normalized area under the peak can be properly used in the excel workbooks to quantify histone PTM abundance. 

Note: The files that the histone PTM quantification excel workbooks are based off of are from Kidney/Experiment1. 

Note: The "custom sort" function in excel does not permit a list long enough to include all ~700 peptides, which is why a solution in R is necessary.

Importing Libraries: 
```{r}
library(tidyverse)
```

## Correcting the order of all Ambic files

Creating vectors that contain the desired order for each DIA assay library, based on Kidney/Exp1 order:

```{r}
Target_Ambic <- c(
"ASRLAQ[+1]YNK[+57]RSTITSRE",
"ASRLAQY[-18]N[+1]KR[+28]STITSRE",
"ASRLAQYNKRSTITSR[+14]E[-1]",
"AS[-18]R[+28]LAQYN[+1]KRSTITSRE",
"ASRLAQY[+32]N[+1]KRSTITSRE",
"ASRLAQYNK[+32]R[+1]STITSRE",
"ASRLAQYN[+1]KRSTITSRE",
"ASR[+14]LAQY[-18]N[+16]KRSTITSRE",
"A[+57]S[-18]RLAQ[+1]YNKRSTITSRE",
"ASRLAQYNK[+32]R[+28]STITSRE",
"A[+43]S[-18]R[+28]LAQYNKRSTITSRE",
"ASRLAQY[-18]NK[+72]R[+14]STITSRE",
"AS[+80]RLAQY[-18]NKR[+1]STITSRE",
"ASRLAQY[-18]NK[+72]RSTITSRE",
"AS[-18]R[+28]LAQ[+1]YNKRSTITSRE",
"ASRLAQY[+16]NK[+43]R[+1]STITSRE",
"ASRLAQYN[+1]K[+14]R[+32]STITSRE",
"AS[-18]R[+28]LAQYNKRSTITSRE",
"ASRLAQY[-18]NK[+14]R[+16]STITSRE",
"ASRLAQYNKRSTITSRE",
"A[+43]SR[+16]LAQ[+1]YNKRSTITSRE",
"ASRLAQ[+1]YNKRSTITSRE",
"ASRLAQY[+16]NKRSTITSRE",
"ASRLAQY[-18]N[+16]K[+14]RSTITSRE",
"ASRLAQ[+1]YNK[+32]RSTITSRE",
"ASRLAQ[+1]Y[-18]NK[+28]RSTITSRE",
"ASRLAQY[+32]NKRS[-18]TITSRE",
"ASRLAQY[+32]NK[+32]RSTITSRE",
"ASRLAQY[-18]N[+1]K[+28]RSTITSRE",
"ASRLAQ[+1]YNKR[+32]STITSRE",
"ASRLAQYNKR[+16]STITSRE",
"ASRLAQY[-18]NK[+28]R[+1]STITSRE",
"V[+43]QT[+80]AVR[+1]LLLPGELAKHAVSE",
"V[+43]Q[+1]TAVR[+1]LLLPGELAKHAVSE",
"V[+57]QTAVRLLLPGELAKH[+57]AVSE",
"V[+57]QTAVRLLLPGELAK[+57]HAVSE",
"V[+57]QTAVRLLLPGELAKHAVSE",
"VQ[+1]T[+42]AVR[+28]LLLPGE",
"V[+28]Q[+1]TAVR[+32]LLLPGELAKHAVSE",
"V[+57]QTAVRLLLPGE",
"V[+43]QTAVR[+16]LLLPGELAKHAVSE",
"V[+28]QT[+114]AVR[+1]LLLPGELAKHAVSE",
"VQT[-18]AVR[+42]LLLPGE",
"V[+28]Q[+1]TAVR[+16]LLLPGELAKHAVSE",
"VQTAVR[+14]LLLPGELAKHAVSE",
"VQT[-18]AVR[+32]LLLPGELAK[+57]HAVSE",
"VQ[+1]T[-18]AVR[+32]LLLPGELAKHAVSE",
"V[+43]QT[-18]AVRLLLPGELAKHAVSE",
"V[+28]QTAVRLLLPGELAKHAVSE",
"V[+18]QT[-18]AVR[+16]LLLPGELAKHAVSE",
"V[+28]Q[+1]TAVRLLLPGELAKHAVSE",
"VQTAVRLLLPGELAKHAVSE",
"VQTAVR[+14]LLLPGELAKH[+57]AVSE",
"VQT[-18]AVR[+32]LLLPGELAKHAVSE",
"VQT[-18]AVR[+16]LLLPGELAKHAVSE",
"VQTAVR[+14]LLLPGE",
"V[+43]QTAVR[+28]LLLPGELAKHAVSE",
"VQ[+1]TAVR[+14]LLLPGELAKHAVSE",
"VQ[+1]T[+114]AVR[+28]LLLPGELAKHAVSE",
"V[+28]Q[+1]T[+114]AVRLLLPGELAKHAVSE",
"VQTAVR[+16]LLLPGELAKHAVSE",
"V[+57]QTAVRLLLPGELAK[+114]HAVSE",
"S[+42]SAAIALPPPAPAKSPKKRAKSPRKKTGPTVSD",
"VAPAAAPAPATE",
"V[+57]APAAAPAPATE",
"VAPAAAPAP[+16]ATE",
"VAPAAAPAPAT[-18]E[+22]",
"VAPAAAPAPATE[+22]",
"LIVKAVKE",
"LIVKAVK[+42]ESKE[-1]",
"L[+43]IVKAVK[+57]E",
"LIVK[+14]AVK[+32]E",
"LIVKAVK[+43]E",
"LIVKAVKE[+57]",
"L[+43]IVKAVKE",
"LIVK[+57]AVKE",
"LIVKAVK[+57]E",
"L[+57]IVKAVKE",
"LIVK[+43]AVKE",
"LIVKAVKESK[+42]E[-1]",
"L[+43]IVK[+57]AVKE",
"LVARGYD",
"LVARGYDVE",
"RVGAGAPVYLAAVLE[+53.9]",
"RVGAGAPVY[+32]LAAVLE",
"R[+43]VGAGAPVYLAAVLE[+37.9]",
"RVGAGAP[+32]VYLAAVLE",
"R[+57]VGAGAPVYLAAVLE[+37.9]",
"RVGAGAPVYLAAVLE[+61.9]",
"R[+43]VGAGAPVYLAAVLE",
"R[+1]VGAGAPVYLAAVLE[+57]",
"RVGAGAPVY[+16]LAAVLE[+53.9]",
"RVGAGAPVY[+32]LAAVLE[+37.9]",
"RVGAGAPVYLAAVLE[+37.9]",
"RVGAGAPVYLAAVLE[-1]",
"R[+57]VGAGAPVYLAAVLE[+53.9]",
"RVGAGAPVYLAAVLE[+22]Y[-18]LT[+42]AE",
"RVGAGAPVYLAAVLE[+22]Y[-18]LT[+80]AEILE",
"R[+57]VGAGAPVYLAAVLE",
"RVGAGAPVYLAAVLE",
"YLTAEILE[+22]",
"YLTAEILE",
"YLTAE[+22]ILE",
"LAGNAARDNKKTRIIPRHLQLAVRNDEE",
"L[+43]AGNAARD",
"LAGN[+1]AARDNKKTRIIPRHLQLAVRNDEE",
"NKKTRIIPRHLQLAVRNDEE",
"N[+1]KKTRIIPRHLQLAVRNDEE",
"ELNKLLGGVTIAQGGVLPNIQAVLLPKKTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKT[-18]E[+22]KPTKSK",
"LN[+1]K[+16]LLGGVT[-18]IAQGGVLPNIQAVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+42]K[+14]TE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKK[+57]TEKPT[-18]KSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+57]KTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+71]K[+72]TE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+57]KTEKPTKS[-18]K",
"LNKLLGGVTIAQ[+1]GGVLPN[+1]IQAVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+43]PTKS[-18]K",
"LNKLLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPN[+1]IQ[+1]AVLLPKKTEKPTKSK",
"LNK[+57]LLGGVTIAQGGVLPNIQAVLLPKKTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+22]KPTKS[-18]K",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+42]K[+28]TE",
"LNKLLGGVTIAQGGVLP[+32]NIQAVLLPKKT[+80]E",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKSK[-1]",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+28]KTEKPTKSK[-1]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTK[+43]SK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPT[-18]KSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+72]K[+71]TE",
"SYAIYVYKVLKQVHPD",
"SYAIYVYKVLKQVHPDTGISSKAMSIMNSFVND",
"SYAIYVYKVLKQVHPDTGISSKAMS[+114]IMNSFVND",
"SYAIYVYKVLKQVHPDTGISSKAMSIMNSFVND[+57]IFE",
"S[+43]YAIYVYKVLKQVHPD",
"SYAIYVYKVLKQVHPDTGISSK[+42]AMSIMNSF[+32]VNDIFE",
"IFERIAAE",
"I[+57]FERIAAE",
"I[+43]FERIAAE",
"IFER[+16]IAAE",
"R[+1]IAAEASR[+16]LAHYNKRSTITSRE",
"R[+1]IAAEASRLAHYNKRSTITSRE",
"ASRLAHYN[+1]K[+42]R[+1]STITSRE",
"ASRLAHYNK[+57]RSTITSRE",
"ASRLAHYNK[+42]R[+14]STITSRE",
"ASRLAHYNK[+43]R[+16]STITSRE",
"ASRLAHY[-18]NK[+72]RSTITSRE",
"A[+57]SRLAHYNKRSTITSRE",
"A[+57]SRLAHYN[+1]KRSTITSRE",
"ASRLAHYNK[+32]R[+28]STITSRE",
"ASRLAHYNKRS[+44]TITSRE",
"ASRLAHY[-18]N[+16]K[+42]RSTITSRE",
"ASRLAHYN[+1]K[+57]RSTITSRE",
"ASRLAHYNK[+28]R[+32]STITSRE",
"ASRLAHY[-18]NK[+57]RSTITSRE",
"ASRLAHYN[+1]K[+42]RSTITSRE",
"ASRLAHY[+16]NK[+42]RSTITSRE",
"ASRLAHYNK[+42]R[+16]STITSRE",
"ASR[+1]LAHYN[+1]KRSTITSRE",
"ASRLAHYNKRSTITSRE[+57]",
"ASRLAHYNK[+43]R[+1]STITSRE",
"ASRLAHY[+32]NKR[+14]STITSRE",
"AS[+114]RLAHYNKRSTITSRE",
"ASRLAH[+57]Y[-18]N[+16]KRSTITSRE",
"ASRLAHYNK[+42]R[+1]STITSRE",
"A[+43]SRLAH[+57]YNKRSTITSRE",
"ASRLAHY[+32]NK[+14]RSTITSRE",
"A[+43]SR[+1]LAHYNKRSTITSRE",
"A[+57]SRLAHYNKRS[-18]TITSRE",
"A[+43]SRLAHYN[+1]KRSTITSRE",
"ASRLAH[+57]YNKR[+1]STITSRE",
"A[+43]SRLAHYNKRSTITSRE",
"ASRLAHYNK[+28]R[+14]STITSRE",
"ASRLAHYNK[+43]RSTITSRE",
"ASRLAHYNK[+57]RST[-18]ITSRE",
"ASRLAHY[-18]NKRSTITSRE",
"ASRLAH[+57]YNK[+57]RSTITSRE",
"ASRLAHYNKRST[-18]ITSRE",
"ASRLAHYNKRS[+114]TITSRE",
"ASRLAHYNKR[+1]STITSRE",
"ASRLAHYN[+16]K[+42]RSTITSRE",
"ASRLAH[+57]YN[+1]KRSTITSRE",
"ASRLAHYNK[+16]R[+28]STITSRE",
"A[+57]SRLAHYNK[+57]RSTITSRE",
"ASRLAHY[-18]NK[+14]R[+32]STITSRE",
"ASRLAHYNKR[+32]STITSRE",
"ASRLAHY[-18]N[+1]KRSTITSRE",
"ASRLAHY[+32]NKRSTITSRE",
"ASRLAHYN[+16]KRSTITSRE",
"ASRLAHY[+16]N[+1]KRSTITSRE",
"ASRLAHYNKR[+16]STITSRE",
"ASRLAHY[-18]NK[+32]R[+14]STITSRE",
"ASRLAHYNK[+32]RSTITSRE",
"ASRLAHYNKR[+14]S[-18]TITSRE",
"ASRLAHYN[+16]K[+14]R[+1]STITSRE",
"ASRLAHYNKR[+1]ST[-18]ITSRE",
"ASRLAHYNKRS[-18]TITSRE",
"ASRLAHYN[+1]KRSTITSRE",
"ASRLAHYNK[+28]RSTITSRE",
"ASRLAHYNK[+14]R[+1]STITSRE",
"A[+43]SR[+1]LAH[+57]YNKRSTITSRE",
"ASRLAHY[-18]NKR[+1]STITSRE",
"A[+57]SR[+1]LAHYNKRSTITSRE",
"ASRLAHYNK[+72]R[+28]STITSRE",
"AS[-18]RLAHYNKRSTITSRE",
"ASRLAHYNK[+114]RSTITSRE",
"ASR[+28]LAHYNKRSTITSRE",
"ASRLAHY[+16]NKRSTITSRE",
"ASR[+1]LAHYNKRSTITSRE",
"ASRLAHYNKRSTITSRE",
"ASRLAHYNKRSTIT[-18]SRE",
"ASRLAHYNKRSTITSRE[-1]",
"ASRLAH[+57]YNKRSTITSRE",
"AS[-18]R[+16]LAHYN[+1]KRSTITSRE",
"I[+43]QTAVRLLLPGELAKHAVSE",
"I[+57]Q[+1]TAVRLLLPGE",
"I[+57]Q[+1]TAVR[+16]LLLPGELAKHAVSE",
"IQTAVRLLLPGE[+22]",
"I[+57]QT[-18]AVRLLLPGELAKHAVSE",
"I[+57]QTAVRLLLPGE",
"IQTAVRLLLPGELAKHAVSE[+53.9]",
"I[+57]QTAVR[+1]LLLPGELAKHAVSE",
"I[+43]Q[+1]TAVR[+1]LLLPGELAKHAVSE",
"I[+57]Q[+1]TAVRLLLPGELAKHAVSE",
"I[+57]QTAVRLLLPGELAKHAVSE",
"IQTAVRLLLPGELAK[+72]HAVSE",
"I[+43]QTAVRLLLPGELAK[+114]HAVSE",
"I[+43]QTAVRLLLPGELAKH[+57]AVSE",
"IQTAVRLLLPGELAKHAVS[+80]E[-1]",
"I[+57]QTAVRLLLPGELAKH[+57]AVSE",
"I[+57]QTAVRLLLPGELAKHAVSE[+57]",
"I[+57]QTAVR[+1]LLLPGE",
"I[+57]QTAVRLLLPGELAK[+57]HAVSE",
"IQTAVRLLLPGE[+53.9]LAKHAVSE",
"I[+43]Q[+1]T[+80]AVRLLLPGELAKHAVSE",
"I[+28]QTAVR[+32]LLLPGE",
"IQ[+1]T[-18]AVR[+1]LLLP[+16]GELAKHAVSE",
"IQTAVRLLLPGELAK[+43]HAVSE",
"I[+43]QTAVRLLLPGELAK[+57]HAVSE",
"I[+43]QTAVRLLLPGE",
"IQTAVRLLLPGELAK[+114]HAVSE",
"IQ[+1]T[+42]AVR[+14]LLLPGE",
"IQT[+42]AVRLLLPGE",
"I[+57]QTAVRLLLPGE[+57]LAKHAVSE",
"IQTAVR[+32]LLLPGE",
"IQ[+1]T[+42]AVRLLLPGE",
"I[+57]QTAVRLLLPGE[+61.9]LAKHAVSE",
"IQ[+1]T[+114]AVR[+14]LLLPGE[+57]LAKHAVSE",
"IQ[+1]TAVR[+14]LLLP[+16]GELAKHAVSE",
"I[+43]QTAVR[+14]LLLPGELAKHAVSE",
"I[+57]QTAVRLLLPGELAK[+114]HAVSE",
"IQT[+42]AVR[+1]LLLPGE",
"IQTAVRLLLP[+16]GELAK[+32]HAVSE",
"IQTAVRLLLP[+32]GELAK[+42]HAVSE",
"I[+57]Q[+1]T[+114]AVRLLLPGELAKHAVSE",
"IQ[+1]TAVRLLLPGELAKHAVSE",
"IQTAVR[+1]LLLPGELAKHAVSE",
"IQ[+1]T[-18]AVRLLLPGE[-1]",
"IQ[+1]TAVRLLLPGELAKH[+57]AVSE",
"IQT[-18]AVRLLLPGELAKHAVSE",
"IQ[+1]T[-18]AVRLLLPGELAKHAVSE",
"IQTAVR[+1]LLLPGE",
"IQTAVRLLLPGE[-1]",
"IQTAVRLLLPGELAK[+32]HAVS[-18]E",
"IQ[+1]TAVRLLLPGE",
"I[+57]QT[+114]AVR[+1]LLLPGELAKHAVSE",
"I[+57]QT[+114]AVRLLLPGELAKHAVSE",
"IQTAVRLLLPGELAKHAVSE[+22]",
"IQTAVRLLLPGELAKHAVSE[-1]",
"IQTAVRLLLPGE",
"IQTAVR[+1]LLLPGE[+22]LAKHAVSE",
"IQTAVRLLLP[+32]GELAKHAVS[-18]E",
"I[+28]QTAVRLLLPGELAKHAVSE",
"IQTAVRLLLPGELAK[+28]HAVSE",
"IQTAVRLLLPGE[+22]LAKHAVSE",
"IQTAVRLLLP[+16]GELAKHAVSE",
"IQ[+1]T[-18]AVRLLLP[+16]GELAKHAVSE",
"IQTAVRLLLPGELAKHAVSE",
"IQTAVRLLLPGELAKHAVS[-18]E",
"IQTAVR[+1]LLLPGELAKHAVSE[-1]",
"IQTAVR[+16]LLLPGELAKHAVSE",
"IQTAVRLLLPGELAKHAVSE[+44]",
"IQTAVRLLLPGELAK[+57]HAVSE",
"IQTAVRLLLPGELAKHAVSE[+37.9]",
"IQTAVRLLLPGELAKH[+57]AVS[-18]E",
"IQTAVRLLLPGELAKH[+57]AVSE",
"IQTAVRLLLPGELAKHAVSE[+52.9]",
"IQTAVRLLLP[+32]GELAK[+28]HAVSE[-1]",
"IQTAVRLLLPGELAK[+14]HAVS[+44]E",
"IQTAVRLLLPGE[+57]LAKHAVSE",
"IQTAVRLLLPGELAK[+57]HAVS[-18]E",
"IQTAVR[+1]LLLPGELAK[+57]HAVSE",
"IQTAVRLLLP[+32]GELAK[+57]HAVSE",
"IQTAVRLLLPGELAKH[+61.9]AVSE",
"IQTAVRLLLPGE[+22]LAKH[+57]AVSE",
"IQTAVRLLLP[+16]GELAK[+28]HAVSE",
"IQTAVRLLLP[+16]GELAK[+72]HAVSE",
"IQTAVRLLLP[+16]GELAK[+71]HAVSE",
"IQTAVRLLLPGELAKHAVS[-18]E[+57]",
"IQTAVRLLLP[+32]GELAKHAVSE",
"IQTAVRLLLP[+32]GELAK[+28]HAVSE",
"IQ[+1]T[+114]AVR[+14]LLLPGELAKHAVSE",
"IQTAVRLLLPGELAK[+114]H[+57]AVSE",
"IQTAVRLLLP[+16]GELAK[+42]HAVSE",
"IQTAVRLLLPGELAKHAVSE[+57]",
"L[+43]AKHAVSE",
"LAK[+42]HAVS[-18]E",
"LAK[+16]HAVS[+80]EGT[-18]KAVTKYTSSK",
"LAK[+43]HAVSE",
"GTKAVTK[+43]YTSSK",
"G[+43]TK[+16]AVTKYTSSK",
"G[+43]TKAVTKYTSSK",
"GTK[+43]AVTKYTSSK",
"GTKAVTK[+57]YTSSK",
"GTKAVT[+114]K[+57]Y[+80]TSSK",
"GTK[+57]AVTKYTSSK",
"G[+43]TK[+43]AVTKYTSSK",
"G[+28]TK[+16]AVTKYTSSK",
"GTK[+42]AVTKYTSSK",
"GTKAVT[-18]K[+72]Y[-18]TSSK",
"GTKAVTKYTSSK[+53.9]",
"GT[+114]K[+43]AVTKYTSSK",
"GTKAVTK[+14]Y[+32]TSSK",
"GTKAVTKYTSSK",
"G[+57]TKAVTKYTSSK",
"GTK[+43]AVTK[+43]YTSSK",
"LN[+1]KLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNK[+43]LLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+57]KTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+57]KPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+16]K[+43]TEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK[+57]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVK[+57]AK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKK[+57]TEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+57]PVKAK",
"LNK[+114]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LN[+1]K[+16]LLGGVT[-18]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQ[+1]AVLLPKK[+28]TEKPVKAK",
"LNK[+14]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPN[+1]IQ[+1]AVLLPKKTEKPVKAK",
"L[+43]NK[+43]LLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEKPVKAK",
"LNK[+43]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVK[+57]AK",
"LNKLLGGVTIAQ[+1]GGVLPN[+1]IQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLP[+32]NIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLP[+16]N[+1]IQ[+1]AVLLPKKTEKPVKAK",
"L[+57]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVT[-18]IAQ[+1]GGVLPNIQAVLLPKKTEKPVKAK",
"LN[+16]K[+43]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"L[+43]NK[+16]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVT[-18]IAQGGVLP[+32]NIQAVLLPKKTEKPVKAK",
"LN[+1]KLLGGVT[-18]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPN[+1]IQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLP[+16]K[+43]KTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLP[+32]K[+28]KTEKPVKAK",
"LNK[+57]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"L[+43]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNK[+43]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNQLLRGVTISN[+1]GGVLPRIHPE",
"SIGIYLQ[+1]E",
"MAGGK[+14]AGKD[-18]",
"LNKLLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKAK[+114]",
"LN[+1]K[+16]LLGGVT[-18]IAQGGVLPNIQAVLLPKKTEKAK",
"A[+43]EVAPAPAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"A[+42]EVAPAPAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"A[+42]EVAPAPAAAPAKPAKKKASK[+57]PKKTGPSVSDQILKVVTASKE",
"AEVAPAPAAAPAKPAKKKASKPKKTGPSVSDQ[+1]ILKVVTASKE",
"AEVAPAPAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"A[+43]EVAPAPAAAPAKPAKKKASK[+57]PKKTGPSVSDQILKVVTASKE",
"A[+28]EVAP[+16]APAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"AEVAPAPAAAPAKPAKKKASKPK[+57]KTGPSVSDQILKVVTASKE",
"V[+43]APAPAAAPAKPAKK[+57]KASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAP[+16]AK[+42]PAKKKASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAPAKPAKKK[+42]ASK[+16]PKKTGPSVSDQILKVVTASKE",
"V[+42]AP[+16]APAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAPAKPAKK[+57]KASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAPAKPAKKK[+57]ASKPKKTGPSVSDQILKVVTASKE",
"V[+43]APAPAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"V[+43]APAPAAAP[+16]AKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAPAK[+16]PAKKKASK[+42]PKKTGPSVSDQILKVVTASKE",
"V[+57]APAPAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAPAKPAKKKAS[+44]K[+14]PKKTGPSVSDQILKVVTASKE",
"VAPAPAAAPAKPAKKKASKPKKTGPSVSDQ[+1]ILKVVTASKE",
"VAPAPAAAP[+16]AK[+28]PAKKKASKPKKTGPSVSDQILKVVTASKE",
"Q[+226.1]ILK[+28]VVTASKE",
"Q[+1]ILKVVTASKE",
"QILK[+14]VVT[-18]ASKE",
"Q[+57]ILKVVTASKE",
"QILKVVTASKE",
"Q[-17]ILKVVTASKE",
"R[+71]KGVSLAALK[+72]KALAAGGYD",
"RKGVSLAALK[+16]K[+42]ALAAGGYDVE",
"RKGVSLAALKKALAAGGY[-18]DVE",
"RK[+42]GVSLAALK[+72]KALAAGGYDVE",
"RKGVSLAALKKALAAGGYDVE[+53.9]",
"RKGVSLAALKKALAAGGYDVE[+52.9]",
"RKGVSLAALKKALAAGGYDVE[+37.9]",
"RKGVSLAALK[+42]K[+42]ALAAGGYDVE",
"RKGVSLAALKK[+16]ALAAGGY[+80]DVE",
"RKGVSLAALK[+71]K[+72]ALAAGGYD",
"RK[+114]GVSLAALKKALAAGGYDVE",
"RKGVSLAALK[+72]K[+71]ALAAGGYD",
"R[+57]KGVSLAALKK[+57]ALAAGGYDVE",
"RKGVSLAALKK[+43]ALAAGGYD[+57]VE",
"RKGVSLAALK[+72]K[+43]ALAAGGYDVE",
"R[+28]KGVS[+86]LAALKKALAAGGYDVE",
"RK[+43]GVSLAALK[+57]KALAAGGYDVE",
"RKGVS[+114]LAALKKALAAGGYDVE",
"RKGVSLAALKK[+114]ALAAGGYD[+57]VE",
"RKGVSLAALK[+43]K[+72]ALAAGGYDVE",
"R[+57]K[+14]GVSLAALK[+72]KALAAGGYD",
"RKGVSLAALK[+72]K[+72]ALAAGGYD",
"RKGVSLAALKKALAAGGY[+16]DVE",
"RKGVSLAALK[+72]K[+156.1]ALAAGGYD",
"RKGVSLAALK[+156.1]K[+72]ALAAGGYD",
"RKGVSLAALKKALAAGGYD[+53.9]VE",
"R[+1]K[+42]GVSLAALKKALAAGGYDVE",
"RKGVSLAALK[+114]KALAAGGYDVE",
"RKGVSLAALKKALAAGGYDVE[+57]",
"RKGVSLAALK[+57]KALAAGGYDVE",
"RKGVSLAALK[+43]K[+42]ALAAGGYDVE",
"RKGVSLAALKK[+57]ALAAGGYDVE",
"RK[+57]GVSLAALKKALAAGGYDVE",
"RK[+14]GVSLAALKK[+43]ALAAGGYDVE",
"R[+14]KGVSLAALKK[+43]ALAAGGYDVE",
"R[+1]KGVSLAALK[+42]KALAAGGYDVE",
"RKGVSLAALK[+57]K[+28]ALAAGGYDVE",
"R[+43]KGVSLAALKKALAAGGYDVE",
"RK[+43]GVSLAALKKALAAGGYDVE",
"RKGVSLAALKKALAAGGY[+80]D[+16]VE",
"RKGVSLAALKKALAAGGYD[+56]",
"RKGVSLAALKKALAAGGYD[+57]VE",
"R[+43]K[+28]GVSLAALK[+43]KALAAGGYDVE",
"RK[+14]GVSLAALK[+43]KALAAGGYDVE",
"R[+14]KGVSLAALK[+43]KALAAGGYDVE",
"RKGVSLAALKK[+114]ALAAGGYDVE",
"R[+57]KGVSLAALKKALAAGGYDVE",
"RKGVSLAALK[+28]K[+57]ALAAGGYDVE",
"R[+1]KGVSLAALKK[+57]ALAAGGYDVE",
"RKGVSLAALKKALAAGGYDVE",
"RKGVSLAALKKALAAGGYD[+37.9]VE",
"RKGVSLAALKKALAAGGYD[-18]VE",
"KN[+1]NARVKIAIKSLVSKGTLVQTKGTGASGSFKLGKKAAE",
"KNNARVKIAIKSLVSKGTLVQTKGTGASGSFKLGKKAAE",
"KNNARVKIAIKSLVSK[+57]GTLVQTKGTGASGSFKLGKKAAE",
"KNNARVKIAIKSLVSKGTLVQTK[+57]GTGASGSFKLGKKAAE",
"KNN[+1]ARVKIAIKSLVSKGTLVQTKGTGASGSFKLGKKAAE",
"GPSLPKLIVASVTE",
"G[+57]PSLPKLIVASVTE",
"SKERKGTSLAAIKKYLTAKNVD",
"SKERKGTSLAAIKKYLTAKNVDVPKANKRINTAVAKLVE",
"SKERKGTSLAAIKKYLTAKNVDVPKANKRIN[+1]TAVAKLVE",
"RKGTSLAAIKK[+57]YLTAKNVDVPKANKRINTAVAKLVE",
"RKGTSLAAIKKYLTAKNVDVPKAN[+1]KRIN[+1]TAVAKLVE",
"RKGTSLAAIKKYLTAKNVDVPKANKRINTAVAKLVE",
"RKGTSLAAIKKYLTAK[+57]NVDVPKANKRINTAVAKLVE",
"RKGTSLAAIKKYLTAKNVDVPKAN[+1]KRINTAVAKLVE",
"V[+226.1]PK[+28]AN[+1]KRINTAVAKLVE",
"I[+43]RRYQKSTE",
"LLIRKLPFQR[+1]LVRE[-1]",
"LLIR[+1]K[+71]LPFQRLVRE",
"LLIRK[+71]LPFQRLVRE",
"LLIRK[+43]LPFQRLVRE",
"L[+43]LIR[+1]KLPFQRLVRE",
"L[+57]LIRKLPFQRLVRE",
"L[+57]LIRKLPFQ[+1]RLVRE",
"L[+57]LIRK[+57]LPFQRLVRE",
"LLIRK[+114]LPFQRLVRE",
"L[+28]LIR[+16]KLPFQRLVRE",
"LLIRK[+57]LPFQRLVRE",
"L[+43]LIRKLPFQ[+1]RLVRE",
"L[+43]LIRK[+57]LPFQRLVRE",
"LLIR[+16]K[+42]LPFQRLVRE",
"LLIRKLPFQRLVRE",
"L[+57]LIRKLPFQR[+1]LVRE",
"LLIR[+16]KLPFQRLVRE",
"LLIR[+32]KLPFQRLVRE",
"LLIR[+1]KLPFQRLVRE",
"LLIRK[+16]LPFQRLVRE",
"LLIR[+1]K[+14]LPFQRLVRE",
"LLIRK[+32]LPFQRLVRE",
"LLIR[+1]K[+28]LPFQRLVRE",
"L[+57]LIR[+1]KLPFQRLVRE",
"LLIRKLPFQR[+1]LVRE",
"LLIRKLPFQRLVR[+1]E",
"LLIRKLPFQ[+1]RLVRE",
"LLIRKLP[+32]FQRLVRE",
"LLIRKLPFQR[+16]LVRE",
"L[+43]LIRKLPFQRLVRE",
"L[+28]LIRK[+16]LPFQRLVRE",
"IAQDFK[+32]TDLRFQS[-18]SAVMALQE",
"IAQDFKT[-18]DLR[+32]FQSSAVMALQE",
"IAQDFKTDLRFQSSAVMALQE[+57]ASE",
"IAQD[-18]FK[+32]TDLRFQSSAVMALQE",
"IAQDFK[+32]TDLRFQSS[-18]AVMALQE",
"I[+57]AQDFK[+14]TD",
"IAQDFKTDLRF[+32]QSS[-18]AVMALQE",
"IAQDFKTD",
"IAQDFKTDLR[+32]FQS[-18]SAVMALQE",
"IAQDFKTD[-18]LRFQSSAVMALQE",
"IAQDFKTD[+16]LRFQSSAVMALQEASE",
"IAQDFKTDLRFQSSAVMALQEASE[-1]",
"I[+57]AQDFKTDLRFQSSAVMALQE[+57]",
"I[+57]AQDFKTD",
"IAQDFKTDLRF[+32]QSS[-18]AVMALQEASE",
"IAQDFK[+14]TD",
"IAQDFK[+43]TDLR[+14]FQSSAVMALQE",
"IAQDFKTDLRFQSSAVM[+16]ALQE",
"IAQDFKTDLRFQ[+1]SSAVMALQ[+1]E",
"IAQDFK[+18]TD[-18]LRFQSSAVMALQE",
"IAQDFKTDLRFQSSAVMALQ[+1]E",
"IAQDFK[+14]TDLRFQ[+1]SSAVMALQE",
"IAQDFKTDLR[+32]FQSS[-18]AVMALQE",
"IAQDFKTDLRFQSSAVMALQE",
"IAQDFKTDLRFQSSAVM[+16]ALQ[+1]E",
"IAQDFKTDLR[+14]FQSSAVMALQ[+1]EASE",
"IAQDFKTDLRFQS[-18]SAVM[+16]ALQE",
"IAQDFKTDLRFQSSAVMALQ[+1]EASE",
"IAQDFKTDLRFQSSAVM[+16]ALQE[-1]",
"I[+43]AQDFKTD",
"IAQDFK[+14]TD[+57]LRFQSSAVMALQE",
"IAQDFK[+14]TDLR[+1]FQ[+1]SSAVMALQE",
"IAQDFKTD[-18]LR[+32]FQSSAVMALQE",
"IAQDFKTDLR[+16]FQSSAVMALQE",
"IAQDFKTDLRFQSSAVMALQE[+57]",
"IAQDFKTDLR[+14]FQSSAVMALQE",
"IAQDFKTDLR[+1]FQSSAVMALQE[+57]",
"IAQDFKT[-18]DLRF[+32]QSSAVMALQE",
"LRFQSSAVM[+16]ALQE",
"ASEAYLVGLFE",
"ASEAYLVGLFE[+22]",
"ASEAYLVGLFE[-1]",
"AYLVGLFE",
"A[+57]YLVGLFE",
"AYLVGLFE[+22]",
"DTNLC[+57]AIHAKRVTIMPKD",
"DTN[+1]LC[+57]AIHAKRVTIMPKD",
"LKVKRITPRHLQLAIRGDEE",
"LDSLIKATIAGGGVIPHIHK[+43]SLIGKK[+43]GQQKTV",
"LDSLIKATIAGGGVIPHIHKS[+86]LIGKKGQQKTV",
"LDSLIKATIAGGGVIPHIHKSLIGK[+14]KGQ[+1]QKTV",
"LDSLIKATIAGGGVIPHIHKSLIGKK[+14]GQ[+1]QKTV",
"LDSLIKATIAGGGVIPHIHKSLIGK[+14]K[+72]GQQKTV",
"LDSLIKATIAGGGVIPHIHK[+32]SLIGKKGQQKTV[-1]",
"LDSLIKATIAGGGVIPHIHKSLIGKKGQQK[+57]TV",
"LDSLIKATIAGGGVIPHIHKSLIGK[+43]KGQQK[+43]TV",
"LDSLIKATIAGGGVIPHIHK[+57]SLIGKKGQQK[+57]TV",
"LDSLIKATIAGGGVIPHIHK[+14]SLIGKKGQQ[+1]KTV",
"LDSLIKATIAGGGVIPHIHKSLIGKKGQQ[+1]K[+28]TV",
"LDSLIKATIAGGGVIPHIHKSLIGK[+28]KGQ[+1]QKTV",
"LDSLIKATIAGGGVIPHIHKSLIGKKGQ[+1]QK[+28]TV",
"LDSLIKATIAGGGVIPHIHKSLIGK[+43]K[+43]GQQKTV",
"LDSLIKATIAGGGVIPHIHKSLIGKKGQQKTV",
"LDSLIKATIAGGGVIPHIHKSLIGK[+28]KGQQ[+1]KTV",
"LDSLIKATIAGGGVIPHIHK[+28]SLIGKKGQQ[+1]KTV",
"LDSLIKATIAGGGVIP[+16]HIHK[+14]SLIGKKGQQKTV",
"LDSLIKATIAGGGVIPHIHKSLIGKK[+28]GQQ[+1]KTV",
"LDSLIKATIAGGGVIPHIHKSLIGKKGQ[+1]QK[+14]TV",
"LDSLIKATIAGGGVIPHIHKSLIGKKGQQKTV[-1]",
"LDSLIKATIAGGGVIPHIHKSLIGKKGQ[+1]QKTV",
"S[+43]LIK[+72]ATIAGGGVIPHIHKSLIGKKGQQKTV",
"ELN[+1]Q[+1]LLKGVT[+80]IAAGGVLPN[+1]IHPE",
"LNQLLKGVTIAAGGVLPNIHPELLAKKRGAKGKLE",
"EAPAPAP[+32]VP[+32]AKAAKKKKTTASKPKKVGPSVGE",
"L[+57]IVKAVAASKE[+57]",
"LIVKAVAASK[+114]E",
"LIVKAVAAS[+114]KE",
"L[+57]IVKAVAASK[+43]E",
"L[+43]IVKAVAASKE[+22]",
"L[+43]IVK[+114]AVAASKE",
"LIVKAVAASK[+156.1]E",
"LIVK[+43]AVAASKE[+57]",
"LIVK[+57]AVAASK[+43]E",
"L[+43]IVK[+43]AVAASKE",
"LIVK[+43]AVAASK[+57]E",
"L[+57]IVKAVAASK[+57]E",
"LIVKAVAASK[+43]E",
"L[+57]IVKAVAASK[+114]E",
"LIVKAVAASKE[+57]",
"L[+57]IVK[+114]AVAASKE",
"LIVK[+114]AVAASK[+57]E",
"LIVKAVAAS[+44]KE",
"LIVK[+57]AVAASK[+57]E",
"LIVK[+57]AVAASKE",
"LIVKAVAASKE[-1]",
"L[+43]IVKAVAASKE",
"LIVK[+32]AVAASKE",
"LIVK[+43]AVAASKE",
"L[+43]IVK[+57]AVAASKE",
"LIVKAVAASKE",
"LIVKAVAASKE[+22]",
"LIVKAVAASK[+57]E",
"L[+43]IVKAVAASK[+57]E",
"L[+57]IVKAVAASKE",
"RSGVSAAALK[+16]K[+28]ALAAGGYD",
"RSGVSAAALK[+16]KALAAGGYD[+57]",
"RSGVSAAALKK[+42]ALAAGGYD[-1]",
"RSGVSAAALKKALAAGGYD[+57]VD[+57]",
"RSGVSAAALKKALAAGGYDVD",
"RSGVSAAALK[+28]KALAAGGYD",
"RSGVSAAALK[+28]KALAAGGYD[-18]VD",
"RSGVSAAALKK[+14]ALAAGGYD[+16]VD",
"RSGVSAAALK[+156.1]K[+71]ALAAGGYDVD",
"SEEAPAPAPAPAKATK[+28]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAK[+28]ATKKKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKATKK[+28]KTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKATKKK[+28]TTASKPKKVGPSVGE",
"SEEAPAPAPAP[+16]AKATKKKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKATK[+57]K[+42]KTTASKPKKVGPSVGE",
"SEEAPAPAPAPAK[+28]ATK[+72]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAK[+57]ATK[+42]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAT[+80]K[+71]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKATK[+156.1]KKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKTTVS[+86]KPKKVGPSVGE",
"SEEAPAPAPAPAKAAKKKKTTASKPKKVGPSVGE",
"S[+43]EEAPAPAPAPAKAAK[+57]KKKTTASKPKKVGPSVGE",
"S[+44]EEAPAPAPAPAKAAKKKKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKK[+57]KTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKK[+57]TTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKK[+43]KTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKK[+57]KKTTASK[+57]PKKVGPSVGE",
"S[+43]EEAPAPAPAPAKAAKKKK[+57]TTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAK[+43]AAKKKKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKK[+57]KKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAK[+57]KKKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAK[+43]AAKKK[+18]KTTASKPKKVGPSVGE",
"S[+43]EEAPAPAPAPAKAAKKK[+57]KTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKKKK[+114]TTASKPKKVGPSVGE",
"S[+43]EEAPAPAPAPAK[+57]AAKKKKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKK[+43]K[+18]KTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKKK[+114]KTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKKTTASK[+57]PKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKK[+43]TTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKK[+43]KKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKKTTASK[+43]PKKVGPSVGE",
"SEEAPAPAPAPAKAAKKKK[+57]TTASKPKKVGPSVGE",
"SEEAPAPAPAPAK[+57]AAKKKKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKKK[+57]KTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKK[+57]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKKKKTTASKPKK[+57]VGPSVGE",
"SEEAPAPAPAPAKAAK[+43]K[+18]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAK[+57]KKKTTASKPKKVGPSVGE",
"S[+43]EEAPAPAPAPAKAAKKKKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKKKKTTASK[+57]PKKVGPSVGE",
"SEEAPAPAPAPAKAAKK[+114]KKTTASKPKKVGPSVGE",
"EAPAPAPAP[+32]AK[+57]AAKKKKTTASKPKKVGPSVGE",
"EAPAPAPAPAKAAK[+57]K[+32]KKTTASKPKKVGPSVGE",
"E[+61.9]APAPAPAPAK[+43]AAKKKKTTASKPKKVGPSVGE",
"MS[-18]EEAPAPAPAPAK[+114]AAKKKTTASKPKKVGPSVGE",
"MSEEAPAPAPAPAKAAKKKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKK[+43]KTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKT[+114]TASKPKKVGPSVGE",
"S[+43]EEAPAPAPAPAKAAKKKTTASK[+57]PKKVGPSVGE",
"SEEAPAPAPAPAKAAKKKTTASK[+57]PKKVGPSVGE",
"SEEAPAPAPAPAK[+57]AAKKKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKKKTTASKPKKVGPSVGE",
"S[+122]EEAPAPAPAPAKAAKKKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKKKTTASK[+114]PKKVGPSVGE",
"S[+123]EEAPAPAPAPAKAAKKKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAK[+114]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKK[+57]KTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAK[+57]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKKK[+57]TTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKKKTTASKPK[+57]KVGPSVGE",
"SEEAPAPAPAPAK[+114]AAKKK[+18]TTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKK[+57]TTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKK[+57]KTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKTTASKPK[+114]KVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKTTASK[+57]PKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKK[+114]TTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKK[+114]KTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAK[+43]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAP[+16]AK[+28]AAKKKTTASKPKKVGPSVGE",
"S[+80]EEAPAPAPAPAKAAKKKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAKK[+114]KTTASKPKKVGPSVGE",
"SEEAPAPAPAPAK[+114]AAK[+18]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAK[+114]K[+18]KTTASKPKKVGPSVGE",
"SEEAPAPAPAPAKAAK[+114]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAK[+14]AAK[+114]KKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAK[+18]AAK[+114]KKTTASKPKKVGPSVGE",
"S[+43]EEAPAPAPAPAKAAKKKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKK[+43]KTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAK[+57]AAKKKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAK[+43]AAKKKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKK[+43]TTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAK[+57]KKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKTTASKPKK[+57]VGPSVGE",
"SEEAPAPAPAPAK[+43]AAKKKTTASKPKKVGPSVGE",
"SEEAPAPAPAPAK[+71]AAK[+114]KKTTASKPKKVGPSVGE",
"S[+43]EEAPAPAPAPAKAAKK[+57]KTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKTTAS[+114]KPKKVGPSVGE",
"S[+43]EEAPAPAPAPAKAAK[+57]KKTTASKPKKVGPSVGE",
"S[+43]EEAPAPAPAPAK[+57]AAKKKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAKAAKKKTTASK[+114]PKKVGPSVGE",
"S[+43]EEAPAPAPAPAKAAKKK[+57]TTASKPKKVGPSVGE",
"S[+44]EEAPAPAPAPAKAAKKKTTASKPKKVGPSVGE",
"S[+42]EEAPAPAPAPAK[+114]AAKKKTTASKPKKVGPSVGE",
"E[+226.1]APAPAPAPAK[+72]AAKKKTTASKPKKVGPSVGE",
"E[+283.1]AP[+16]APAPAPAKAAKKKTTASKPKKVGPSVGE",
"APAPAPAPAKAAKKKTTASKPKKVGPSVGE",
"ETPAPAPAPAK[+43]AAK[+32]KKKTTASKPKKVGPSVGE",
"ETPAPAPAPAK[+16]AAK[+43]KKKTTASKPKKVGPSVGE",
"ETPAPAPAP[+16]AK[+43]AAKKKKTTASKPKKVGPSVGE",
"E[+42]TPAPAPAPAKAAKK[+32]KKTTASKPKKVGPSVGE",
"ETPAPAPAPAKAAKK[+32]K[+43]KTTASKPKKVGPSVGE",
"ETPAPAPAP[+16]AKAAK[+43]KKKTTASKPKKVGPSVGE",
"ETPAPAPAPAKAAK[+32]K[+43]KKTTASKPKKVGPSVGE",
"ETPAPAPAP[+32]AK[+43]AAKKKKTTASKPKKVGPSVGE",
"IQTAVRLLLP[+32]AAE[+22]",
"IQTAVRLLLP[+16]AAE[+22]",
"IQTAVRLLLP[+32]AAE",
"IQTAVRLLLPAAE[+22]",
"LNKLLGRVTIAQGGVLPNIQAVLLPK[+71]K[+156.1]TEKAK",
"ET[-18]RGVLKVFLE",
"ETRGVLK[+57]VFLE",
"ETRGVLK[+114]VFLE",
"ET[+42]R[+1]GVLKVFLE",
"E[+43]TRGVLKVFLE",
"ETRGVLKVFLE",
"E[+57]T[-18]RGVLKVFLE",
"ET[-18]RGVLK[+57]VFLE",
"ET[-18]R[+14]GVLK[+16]VFLE",
"TRGVLK[+43]VFLE",
"T[+42]R[+1]GVLKVFLE",
"TRGVLKVFLE[+37.9]",
"TRGVLKVFLE[-1]",
"TR[+32]GVLK[+42]VFLE[+61.9]NVIRDAVTYTE",
"TRGVLK[+57]VFLE",
"T[+42]R[+16]GVLKVFLE",
"T[+43]RGVLKVFLE",
"TRGVLK[+114]VFLE",
"TRGVLKVFLE[+57]",
"TRGVLK[+16]VFLE",
"TRGVLKVFLE",
"TRGVLKVF[+32]LE",
"T[+57]RGVLKVFLE",
"T[+28]RGVLK[+71]VFLE[+37.9]NVIRDAVTYTE",
"T[+114]RGVLKVFLE",
"TR[+1]GVLK[+42]VFLE",
"TRGVLKVFLE[+44]",
"N[+43]VIRDAVTYTE",
"NVIR[+1]DAVTYTE",
"N[+1]VIRDAVT[+42]YTE",
"N[+58]VIRDAVTYTE",
"N[+1]VIRDAVTYTE",
"N[+1]VIR[+14]DAVT[+42]YTE",
"NVIRD[-18]AVTYTE",
"NVIRDAVTYTE[-1]",
"NVIRDAVTY[-18]T[+42]E[+22]",
"N[+43]VIRDAVTYTE[+22]",
"NVIRDAVTYT[-18]E[+22]",
"NVIRDAVTYTEHAK[+32]RKTVTAMD[-1]",
"NVIRDAVTYTEHAK[+32]RKTVTAMD",
"NVIRDAVTYTEHAK[+43]RKTVTAMD",
"NVIRDAVTYTEHAKRK[+43]TVTAMD",
"NVIR[+16]DAVTY[-18]TE",
"NVIRDAVTYTE[+22]",
"N[+43]VIRDAVTYTE[-1]",
"N[+57]VIRDAVTYTE",
"NVIRD[+57]AVTYTE",
"NVIR[+1]DAVT[+42]YTE",
"NVIRDAVT[-18]Y[-18]T[+42]E",
"NVIRDAVTYTE",
"N[+43]VIRDAVT[-18]Y[+32]TE",
"N[+43]VIRDAVTY[+16]TE",
"NVIRDAVTYTE[+44]",
"NVIRDAVTY[+32]T[-18]E",
"NVIRDAVTY[+16]TE",
"N[+57]VIRDAVTY[+16]TE",
"NVIRDAVTYTE[+37.9]",
"NVIRDAVT[-18]YTE",
"HAKRKTVTAMDVVYSFGG",
"HAKRKTVTAMD[-18]"
)
```


#Sorting Ambic Files: 

Gills/Ambic/Exp1

```{r}
Gills_Ambic_Exp1 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Gills_Ambic_Exp1.csv")

Sorted_Gills_Ambic_Exp1 <- Gills_Ambic_Exp1[match(Target_Ambic, Gills_Ambic_Exp1$`Peptide Modified Sequence`),]

write_csv(Sorted_Gills_Ambic_Exp1, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Gills_Ambic_Exp1.csv")
```

Kidney/Ambic/Exp1

```{r}
Kidney_Ambic_Exp1 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Kidney_Ambic_Exp1.csv")

Sorted_Kidney_Ambic_Exp1 <- Kidney_Ambic_Exp1[match(Target_Ambic, Kidney_Ambic_Exp1$`Peptide Modified Sequence`),]

write_csv(Sorted_Kidney_Ambic_Exp1, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Kidney_Ambic_Exp1.csv")
```

Testes/Ambic/Exp1

```{r}
Testes_Ambic_Exp1 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Testes_Ambic_Exp1.csv")

Sorted_Testes_Exp1 <- Testes_Ambic_Exp1[match(Target_Ambic, Testes_Ambic_Exp1$`Peptide Modified Sequence`),]

write_csv(Sorted_Testes_Exp1, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Testes_Ambic_Exp1.csv")
```

Gills/Ambic/Exp2

```{r}
Gills_Ambic_Exp2 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Gills_Ambic_Exp2.csv")

Sorted_Gills_Exp2 <- Gills_Ambic_Exp2[match(Target_Ambic, Gills_Ambic_Exp2$`Peptide Modified Sequence`),]

write_csv(Sorted_Gills_Exp2, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Gills_Ambic_Exp2.csv")
```


Kidney/Ambic/Exp2

```{r}
Kidney_Ambic_Exp2 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Kidney_Ambic_Exp2.csv")

Sorted_Kidney_Exp2 <- Kidney_Ambic_Exp2[match(Target_Ambic, Kidney_Ambic_Exp2$`Peptide Modified Sequence`),]

write_csv(Sorted_Kidney_Exp2, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Kidney_Ambic_Exp2.csv")
```


Testes/Ambic/Exp2

```{r}
Testes_Ambic_Exp2 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Testes_Ambic_Exp2.csv")

Sorted_Testes_Exp2 <- Testes_Ambic_Exp2[match(Target_Ambic, Testes_Ambic_Exp2$`Peptide Modified Sequence`),]

write_csv(Sorted_Testes_Exp2, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Testes_Ambic_Exp2.csv")
```



## Correcting the order of all Napho files

Creating vectors that contain the desired order for each DIA assay library, based on Kidney/Exp1 order:

```{r}
Target_Napho <- c(
"RVGAGAPVYLAAVLEYLT[+114]AE[+57]",
"R[+28]VGAGAP[+16]VYLAAVLE",
"RVGAGAPVYLAAVLEYLTAE[+37.9]",
"RVGAGAPVYLAAVLE[+22]",
"R[+57]VGAGAPVYLAAVLE",
"RVGAGAPVYLAAVLE[+57]Y[+80]LT[+114]AEILE",
"RVGAGAP[+16]VYLAAVLE[+22]",
"RVGAGAPVYLAAVLEY[-18]LT[+114]AE",
"RVGAGAPVYLAAVLE[+37.9]YLTAE",
"RVGAGAPVYLAAVLE[+37.9]",
"RVGAGAPVYLAAVLE[+22]YLTAEILE",
"RVGAGAPVYLAAVLE[+57]Y[-18]LTAE",
"RVGAGAPVYLAAVLE[+22]Y[-18]LTAE[+22]ILE",
"RVGAGAPVYLAAVLEYLTAE",
"R[+28]VGAGAPVYLAAVLE",
"RVGAGAPVYLAAVLE[+22]Y[+80]LTAE[+22]ILE",
"R[+43]VGAGAPVYLAAVLE[+22]",
"R[+43]VGAGAP[+32]VY[-18]LAAVLE",
"RVGAGAP[+16]VYLAAVLE",
"RVGAGAPVYLAAVLE[+22]Y[-18]LT[+42]AE",
"R[+42]VGAGAP[+16]VYLAAVLE",
"RVGAGAPVYLAAVLE[+53.9]",
"RVGAGAPVYLAAVLEY[-18]LT[+80]AE[+22]ILE",
"RVGAGAPVYLAAVLE[-1]",
"RVGAGAPVYLAAVLEY[+80]LT[+80]AE",
"RVGAGAPVYLAAVLE",
"RVGAGAPVYLAAVLEY[-18]LT[+80]AEILE[+22]",
"R[+57]VGAGAPVYLAAVLE[+53.9]",
"R[+28]VGAGAP[+16]VYLAAVLE[+22]",
"R[+43]VGAGAPVYLAAVLE[-1]",
"R[+43]VGAGAPVYLAAVLE",
"RVGAGAPVY[-18]LAAVLE[+22]",
"RVGAGAP[+32]VYLAAVLE",
"R[+43]VGAGAPVYLAAVLE[+57]",
"R[+43]VGAGAPVYLAAVLE[+37.9]",
"RVGAGAPVYLAAVLE[+61.9]",
"R[+57]VGAGAPVYLAAVLE[+37.9]",
"R[+43]VGAGAPVYLAAVLE[+53.9]",
"RVGAGAPVYLAAVLEY[+80]LTAE",
"RVGAGAPVYLAAVLEYLTAEILE",
"RVGAGAPVYLAAVLE[+53.9]Y[-18]LTAEILE",
"R[+58]VGAGAPVYLAAVLE",
"YLTAE[+37.9]ILE",
"Y[+43]LTAEILE",
"L[+43]AGNAARD",
"N[+43]KKTRIIPRHLQLAVRNDEE",
"N[+1]KKTRIIPRHLQLAVRNDEE",
"NKK[+43]T[-18]RIIPRHLQLAVRNDEE",
"N[+1]K[+42]KTRIIPRHLQLAVRNDEE",
"N[+43]KKT[-18]RIIPRHLQLAVRNDEE",
"NKK[+43]TRIIPRHLQLAVRNDEE",
"NK[+42]KTR[+1]IIPRHLQLAVRNDEE",
"NKKTRIIPRHLQLAVRNDEE",
"E[+541.1]ELNKLLGGVT[-18]IAQGGVLPNIQAVLLPKKTE",
"L[+28]N[+1]K[+28]LLGGVTIAQGGVLPNIQAVLLPKKTE",
"LNKLLGGVTIAQ[+1]GGVLPN[+1]IQ[+1]AVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+28]KTEKPTKS[-18]K",
"LNKLLGGVTIAQGGVLPN[+1]IQAVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+43]KTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+71]K[+72]TE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+57]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+28]PTKS[-18]K",
"LNKLLGGVTIAQGGVLPNIQAVLLPKK[+43]TE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+57]KPTKS[-18]K",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+53.9]",
"LNK[+114]LLGGVTIAQGGVLPNIQAVLLPKKTEKPTKS[-18]K",
"LNK[+43]LLGGVTIAQGGVLPNIQAVLLPKKTEKPTKS[-18]K",
"L[+43]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPT[-18]KSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+16]K[+43]TE",
"L[+43]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+37.9]",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+71]K[+71]TE",
"LNKLLGGVTIAQGGVLP[+32]NIQAVLLPK[+28]KTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+14]KT[+114]E",
"LNKLLGGVTIAQGGVLP[+16]NIQAVLLPKKTEKPT[-18]KSK",
"LN[+1]KLLGGVT[-18]IAQGGVLPNIQAVLLPKKTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKS[-18]K[+28]",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+28]K[+114]TE",
"LNKLLGGVTIAQGGVLPNIQ[+1]AVLLPKKTEKPTKSK",
"LNK[+42]LLGGVTIAQGGVLPNIQAVLLPKKTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKK[+28]TEKPTKS[-18]K",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+28]PT[-18]KSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPT[-18]KSK[+28]",
"L[+43]NKLLGGVTIAQGGVLPNIQAVLLPKKTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+14]K[+42]TE",
"LNKLLGGVTIAQGGVLP[+32]NIQAVLLPKKTEKPT[-18]KSK",
"LNK[+43]LLGGVTIAQGGVLPNIQAVLLPKKTE",
"LNKLLGGVTIAQ[+1]GGVLPN[+1]IQAVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPN[+1]IQ[+1]AVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKT[-18]EKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+57]KPT[-18]KSK",
"L[+57]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKSK[+42]",
"LN[+1]KLLGGVTIAQGGVLPNIQAVLLPKKTE",
"LNK[+32]LLGGVT[-18]IAQGGVLPNIQAVLLPKKTE",
"LNK[+28]LLGGVTIAQGGVLPNIQAVLLPKKTEKPTKS[-18]K",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+14]KTEKPTKS[-18]K",
"LNKLLGGVTIAQ[+1]GGVLPNIQAVLLPKK[+43]TEKPTKSK",
"LNK[+28]LLGGVTIAQGGVLPNIQAVLLPKKTEKPT[-18]KSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+28]PTKSK",
"LNKLLGGVTIAQGGVLPN[+1]IQ[+1]AVLLPKKTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKSK[+43]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKK[+28]TE[+53.9]",
"L[+43]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKS[-18]K",
"L[+57]NKLLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEKPTKSK",
"L[+57]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+43]PTKSK",
"LNKLLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLP[+32]KKTE[-1]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+37.9]KPT[-18]KSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPT[-18]KSK[+43]",
"LNKLLGGVTIAQ[+1]GGVLPN[+1]IQAVLLPKKTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPT[-18]K[+43]SK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPT[-18]KSK[+114]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPT[-18]KSK",
"L[+57]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKS[-18]K",
"LNK[+43]LLGGVTIAQGGVLPNIQAVLLPKKTEKPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKS[-18]K",
"LNK[+43]LLGGVTIAQGGVLPNIQAVLLPKKTEKPT[-18]KSK",
"LNKLLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEK[+43]PTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+72]K[+71]TE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKT[-18]E[+57]KPTKSK",
"LNKLLGGVTIAQGGVLPN[+1]IQAVLLPKKTEK[+43]PTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKK[+72]TE[+53.9]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+37.9]KPTKS[+44]K",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+14]K[+114]TE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKT[+114]EKPTKS[-18]K",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+114]KTEKPTKS[-18]K",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPTKS[-18]K[+114]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+114]PTKS[-18]K",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+42]KTE",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+57]KPTKSK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+14]KT[+114]EKAK",
"L[+43]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+14]KTEKAK[+43]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+57]KAK",
"LN[+1]K[+42]LLGGVTIAQGGVLPNIQAVLLPKKTEKAK",
"LNKLLGGVTIAQGGVLP[+32]NIQAVLLPKKTEKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+43]AK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+43]KTEKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKK[+43]TEKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKAK[+43]",
"LNKLLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEKAK[+43]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+22]KAK[-1]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKT[-18]E[+57]KAK",
"LNK[+43]LLGGVTIAQGGVLPNIQAVLLPKKTEKAK",
"LNKLLGGVTIAQGGVLP[+32]NIQAVLLPKKT[-18]EKAK",
"LNKLLGGVT[-18]IAQGGVLP[+32]NIQAVLLPKKTEKAK",
"LN[+1]KLLGGVT[-18]IAQGGVLPNIQAVLLPKKTEKAK",
"LNKLLGGVTIAQGGVLPN[+1]IQAVLLPKKTEKAK",
"LNKLLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEKAK",
"LN[+1]KLLGGVTIAQGGVLPNIQAVLLPKKTEKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+156.1]AK[+43]",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+156.1]K[+42]TEKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+42]KTEK[+156.1]AK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKK[+42]TEK[+156.1]AK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKK[+114]T[+80]EKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+57]KAK[+72]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKAK[+114]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKAK[+42]",
"L[+57]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKAK",
"ELNK[+226.1]LLGGVT[+114]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVT[-18]IAQ[+1]GGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLP[+32]NIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVK[+43]AK[+43]",
"LN[+1]K[+14]LLGGVT[+80]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"L[+43]NKLLGGVTIAQGGVLPN[+1]IQ[+1]AVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+57]KPVK[+43]AK",
"L[+57]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+37.9]KPVKAK[-1]",
"L[+43]NKLLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQ[+1]AVLLPKKTEK[+14]PVKAK",
"L[+43]NKLLGGVTIAQ[+1]GGVLPN[+1]IQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKK[+72]TEK[+42]PVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+14]PVKAK[+43]",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+14]PVK[+43]AK",
"LNKLLGGVTIAQGGVLP[+16]NIQAVLLPKKTEKPVKAK[+43]",
"LNKLLGGVTIAQGGVLP[+32]NIQAVLLPKKTEK[+14]PVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+16]K[+42]TEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+43]KTEKP[+16]VKAK",
"L[+43]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+53.9]KPVKAK[-1]",
"L[+28]NK[+72]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"L[+57]NKLLGGVTIAQGGVLP[+16]N[+1]IQAVLLPKKTEKPVKAK",
"LNK[+71]LLGGVTIAQGGVLP[+32]NIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+541.1]K[+28]TEKPVKAK",
"L[+226.1]NK[+226.1]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+16]K[+43]TEKPVKAK",
"LN[+1]KLLGGVT[-18]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+114]PVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+71]K[+43]TEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+43]KTEKPVKAK[+43]",
"LNK[+16]LLGGVT[+80]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+57]KPVKAK",
"LNK[+43]LLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEKPVKAK",
"LN[+1]KLLGGVT[-18]IAQ[+1]GGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+43]PVKAK[+43]",
"LNKLLGGVT[+80]IAQGGVLPNIQAVLLPKKT[+80]EKPVKAK",
"LNK[+42]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKT[-18]EKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+57]KPVKAK[+43]",
"L[+57]N[+1]K[+42]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVT[+80]IAQGGVLP[+32]N[+1]IQAVLLPKKTEKPVKAK",
"L[+57]NKLLGGVTIAQGGVLPN[+1]IQ[+1]AVLLPKKTEKPVKAK",
"LNK[+43]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPK[+43]K[+43]TEKPVKAK",
"LNKLLGGVTIAQGGVLP[+32]NIQAVLLPKKT[-18]EKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLP[+32]K[+28]KTEKPVKAK",
"LNK[+43]LLGGVTIAQGGVLPNIQAVLLPKKTEK[+43]PVKAK",
"LNKLLGGVTIAQ[+1]GGVLPN[+1]IQAVLLPKKTEKPVKAK",
"LNK[+43]LLGGVTIAQGGVLPNIQAVLLPK[+43]KTEKPVKAK",
"L[+43]NKLLGGVTIAQGGVLPNIQAVLLPK[+43]KTEKPVKAK",
"L[+43]NKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+43]PVKAK",
"LNK[+14]LLGGVT[-18]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQ[+1]AVLLPK[+28]KTEKPVKAK",
"LN[+1]K[+28]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNK[+28]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+22]KPVKAK[-1]",
"LNKLLGGVTIAQGGVLPN[+1]IQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKK[+14]TEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEK[+28]PVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKT[-18]E[+22]KPVKAK",
"LNKLLGGVTIAQ[+1]GGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLP[+16]N[+1]IQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQ[+1]AVLLPK[+14]KTEKPVKAK",
"L[+28]N[+1]KLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVT[-18]IAQGGVLP[+32]NIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"L[+57]NKLLGGVTIAQGGVLPN[+1]IQAVLLPKKTEKPVKAK",
"LNK[+72]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"L[+28]NK[+28]LLGGVT[-18]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"L[+43]N[+1]KLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLP[+16]NIQAVLLPKKTEKPVKAK",
"L[+43]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK[+43]",
"LN[+1]K[+16]LLGGVT[-18]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVT[+80]IAQ[+1]GGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQ[+1]GGVLPN[+1]IQ[+1]AVLLPKKTEKPVKAK",
"L[+43]NKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVK[+43]AK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTE[+22]KPVKAK",
"LNKLLGGVTIAQGGVLPN[+1]IQ[+1]AVLLPKKTEKPVKAK",
"L[+43]NKLLGGVTIAQGGVLP[+16]N[+1]IQAVLLPKKTEKPVKAK",
"LNK[+43]LLGGVTIAQ[+1]GGVLPN[+1]IQAVLLPKKTEKPVKAK",
"LN[+1]KLLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LN[+1]K[+14]LLGGVTIAQGGVLP[+32]NIQAVLLPKKTEKPVKAK",
"LNK[+71]LLGGVT[-18]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"LN[+1]K[+16]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNK[+14]LLGGVTIAQGGVLP[+32]NIQAVLLPKKTEKPVKAK",
"LN[+1]K[+32]LLGGVT[-18]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"L[+43]NK[+16]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNK[+43]LLGGVTIAQGGVLPNIQAVLLPKKTE[+22]KPVKAK",
"LN[+1]K[+42]LLGGVTIAQGGVLPNIQAVLLPKKTEKPVKAK",
"LNKLLGGVTIAQGGVLPNIQAVLLPKKTEKPVK[+32]AK[+32]",
"LN[+1]KLLGGVT[+80]IAQGGVLPNIQAVLLPKKTEKPVKAK",
"SYAIYVYKVLKQVHPDTGISS[+114]KAMSIMNSFVNDIFE",
"SYAIYVYKVLKQVHPDTGISSKAM[+16]SIMNSFVND",
"SYAIYVYKVLKQVHPD",
"SYAIYVYKVLKQVHPD[+57]",
"S[+57]YAIYVYKVLKQVHPD",
"SYAIYVYKVLKQVHPDTGISSKAMS[+114]IMNSFVNDIFE",
"SYAIYVYKVLKQVHPDTGISSK[+42]AMSIMNSFVNDIFE[-1]",
"SYAIYVYKVLKQVHPD[+57]TGISSK[+43]AMSIMNSFVNDIFE",
"SYAIYVYKVLKQVHPDTGISSK[+42]AMSIMNSFVND[+57]IFE",
"SYAIYVYKVLKQVHPDTGISSK[+43]AMSIM[+16]NSFVNDIFE",
"SYAIYVYKVLKQVHPDTGISSK[+32]AMSIMNSFVND[-1]",
"SYAIYVYKVLKQVHPD[+57]TGISSKAMSIMNSFVND",
"SYAIYVYKVLKQVHPDTGISSKAMSIM[+16]NSFVND",
"SYAIYVYKVLKQVHPDTGISSKAMSIMNSFVND",
"SYAIYVYKVLKQVHPDTGISSKAMSIMNSFVND[+57]IFE",
"TGISSKAMSIMNSFVND",
"TGISSKAMSIMN[+1]SFVND",
"IFERIAAE",
"I[+43]FERIAAE",
"R[+16]IAAEASRLAHYNKRSTITSRE",
"R[+1]IAAEAS[-18]R[+14]LAHYNKRSTITSRE",
"ASRLAHYN[+1]KRS[+80]TITSRE",
"ASRLAHYNK[+43]R[+14]STITSRE",
"ASRLAHYN[+1]K[+42]R[+1]STITSRE",
"ASRLAHYN[+1]K[+28]R[+16]STITSRE",
"ASRLAHYNKR[+32]STITSRE",
"ASRLAHYNK[+32]R[+14]STITSRE",
"ASRLAHYNK[+28]R[+16]STITSRE",
"ASRLAHYNK[+43]R[+1]STITSRE",
"ASRLAHY[+80]NKR[+1]STITSRE",
"ASRLAHYN[+1]K[+43]RSTITSRE",
"ASRLAHYNK[+42]R[+1]STITSRE",
"ASRLAHYN[+1]K[+28]R[+32]STITSRE",
"AS[+114]RLAHYNKRSTITSRE",
"ASRLAHYNK[+42]R[+14]STITSRE",
"ASRLAHYNKRSTIT[-18]SRE",
"ASRLAHY[-18]NK[+32]R[+14]STITSRE",
"ASRLAHYNKR[+1]STITSRE",
"ASRLAHYNKRSTITSRE",
"ASRLAHYN[+1]KRSTITSRE",
"ASRLAHYNK[+16]RSTITSRE",
"ASRLAHYNK[+28]R[+28]STITSRE",
"ASRLAHYNK[+42]RS[-18]TITSRE",
"A[+57]SRLAHYNKRSTITSRE",
"ASRLAHYNK[+28]RSTITSRE",
"A[+43]SRLAHY[-18]N[+1]KRSTITSRE",
"A[+43]SRLAHYNKRSTITSRE",
"ASR[+16]LAHYNKRSTITSRE",
"A[+57]SRLAHYN[+1]KRSTITSRE",
"ASRLAHY[-18]NK[+42]R[+28]STITSRE",
"A[+43]SRLAHYNKR[+1]STITSRE",
"AS[+44]R[+1]LAHYNKRSTITSRE",
"A[+43]S[-18]R[+1]LAHYNKRSTITSRE",
"A[+57]SR[+1]LAHYNKRSTITSRE",
"ASRLAHYNK[+42]RSTIT[-18]SRE",
"ASRLAHYN[+1]K[+16]R[+28]STITSRE",
"ASRLAHYNK[+32]RSTITSRE",
"AS[-18]R[+16]LAHYNKRSTITSRE",
"AS[-18]R[+32]LAHY[-18]NKRSTITSRE",
"AS[-18]RLAHYNKRSTITSRE",
"A[+43]SRLAHYNKRS[-18]TITSRE",
"ASRLAHYNKR[+16]STITSRE",
"ASRLAHYNKR[+1]ST[-18]ITSRE",
"ASRLAHYNKR[+1]S[-18]TITSRE",
"ASRLAHY[-18]NK[+14]R[+32]STITSRE",
"ASRLAHY[-18]NKRSTITSRE",
"AS[-18]R[+1]LAHYNKRSTITSRE",
"ASRLAHYNK[+42]R[+16]STITSRE",
"A[+43]SRLAHYN[+1]KRSTITSRE",
"ASR[+1]LAH[+57]YNKRSTITSRE",
"A[+57]SRLAHYNK[+43]RSTITSRE",
"ASRLAHY[-18]NKR[+1]STITSRE",
"A[+43]SRLAHYNKRSTIT[-18]SRE",
"ASRLAH[+57]YNKRSTITSRE",
"ASRLAHYNKRS[-18]TITSRE",
"ASRLAHYNK[+43]RSTITSRE",
"ASRLAH[+57]YN[+1]KRSTITSRE",
"A[+43]SRLAHYNKR[+16]STITSRE",
"A[+43]SRLAH[+57]YNKRSTITSRE",
"ASR[+32]LAHYNKRSTITSRE",
"A[+28]SRLAHYNKRSTITSRE",
"A[+57]S[-18]RLAHYNKRSTITSRE",
"A[+57]SRLAHYNKR[+1]STITSRE",
"ASRLAHY[-18]NKRS[+44]TITSRE",
"I[+57]Q[+1]TAVRLLLPGE",
"IQTAVRLLLPGE[+53.9]LAKHAVSE",
"IQTAVRLLLP[+16]GE",
"I[+43]QTAVRLLLPGELAKHAVSE[+53.9]",
"IQ[+1]TAVRLLLPGELAKH[+57]AVSE",
"IQT[-18]AVR[+16]LLLPGE",
"I[+57]QT[-18]AVRLLLPGE",
"IQTAVRLLLP[+32]GE",
"IQTAVRLLLP[+32]GELAKHAVSE",
"IQTAVRLLLPGE[+22]",
"IQTAVRLLLPGE",
"IQT[-18]AVRLLLPGE",
"IQTAVRLLLPGE[+53.9]",
"I[+57]QTAVRLLLPGELAK[+43]HAVSE",
"I[+57]QTAVRLLLPGELAKHAVSE[+57]",
"I[+57]QTAVRLLLPGE[+57]LAKHAVSE",
"I[+57]QTAVRLLLPGE[+37.9]",
"IQTAVR[+32]LLLPGE",
"IQT[+80]AVRLLLP[+32]GELAKHAVSE",
"I[+57]QTAVRLLLPGE[+22]",
"IQTAVRLLLPGELAK[+43]HAVSE",
"IQ[+1]T[+42]AVR[+14]LLLPGE",
"I[+57]QTAVRLLLPGE[+22]LAKHAVSE",
"I[+57]QTAVRLLLPGE",
"IQTAVRLLLPGELAKHAVSE[+57]",
"I[+57]Q[+1]TAVRLLLPGELAKHAVSE",
"I[+43]QTAVR[+16]LLLPGELAKHAVSE",
"I[+28]Q[+1]TAVR[+28]LLLPGE",
"IQTAVRLLLP[+16]GELAK[+72]HAVSE",
"I[+57]QTAVRLLLPGELAKHAVSE",
"IQTAVRLLLPGELAK[+226.1]HAVSE[+53.9]",
"IQTAVRLLLPGE[+57]LAKHAVSE",
"IQ[+1]T[+114]AVR[+14]LLLPGELAKHAVSE",
"I[+57]QTAVRLLLPGELAKH[+57]AVSE",
"IQTAVR[+1]LLLP[+16]GELAK[+14]HAVSE",
"I[+28]Q[+1]TAVR[+28]LLLPGELAKHAVSE",
"IQTAVRLLLPGELAKH[+57]AVSE",
"I[+43]QTAVRLLLPGE[+22]LAKHAVSE",
"IQ[+1]T[-18]AVRLLLPGE[-1]",
"I[+43]QTAVRLLLPGELAKHAVSE[+22]",
"I[+28]Q[+1]TAVR[+14]LLLPGELAKHAVSE",
"IQTAVRLLLPGELAKHAVSE[+53.9]",
"IQ[+1]TAVRLLLPGELAKHAVSE",
"IQTAVRLLLPGELAK[+42]HAVS[-18]E",
"I[+43]QTAVRLLLPGE",
"IQTAVRLLLPGELAK[+32]HAVS[-18]E",
"IQT[-18]AVR[+16]LLLPGELAKHAVSE",
"IQT[+42]AVRLLLPGE",
"IQTAVRLLLPGELAKHAVSE[+22]",
"IQTAVRLLLPGELAKHAVS[-18]E[+22]",
"IQ[+1]TAVR[+14]LLLP[+16]GELAKHAVSE",
"IQ[+1]TAVR[+1]LLLPGELAKHAVSE",
"I[+43]QTAVRLLLPGE[-1]",
"IQTAVR[+1]LLLPGE[+22]LAKHAVSE",
"IQTAVRLLLPGELAK[+14]HAVSE",
"IQT[+42]AVR[+1]LLLPGE",
"IQTAVRLLLPGE[+22]LAKHAVSE",
"I[+28]Q[+1]TAVR[+14]LLLPGE",
"IQ[+1]T[+42]AVRLLLPGE",
"IQT[-18]AVR[+32]LLLPGELAKHAVSE",
"IQTAVR[+16]LLLPGELAKHAVSE",
"IQTAVR[+1]LLLPGELAKHAVSE",
"IQT[-18]AVR[+1]LLLP[+16]GELAKHAVSE",
"IQTAVRLLLPGE[+37.9]",
"IQTAVRLLLPGE[-1]",
"IQ[+1]TAVRLLLPGE",
"IQT[-18]AVRLLLP[+32]GELAKHAVSE",
"I[+43]QTAVRLLLPGELAKHAVSE",
"IQ[+1]T[+42]AVR[+1]LLLPGE",
"I[+57]QT[-18]AVR[+32]LLLPGELAKHAVSE",
"IQTAVRLLLPGELAK[+32]H[+57]AVS[-18]E",
"IQTAVRLLLPGE[+61.9]LAKHAVSE",
"IQ[+1]TAVRLLLPGELAK[+28]HAVSE",
"I[+43]QTAVRLLLPGELAKH[+57]AVSE",
"IQTAVRLLLPGELAK[+71]HAVSE",
"IQTAVR[+1]LLLPGE",
"I[+28]QTAVRLLLPGELAKHAVSE",
"I[+57]Q[+1]TAVR[+16]LLLPGELAKHAVSE",
"I[+57]QTAVRLLLPGELAK[+32]HAVS[-18]E",
"I[+43]Q[+1]T[-18]AVRLLLPGE",
"I[+57]QTAVRLLLP[+32]GELAKHAVSE",
"IQTAVRLLLPGELAK[+28]HAVSE[+22]",
"IQTAVRLLLPGELAKHAVS[-18]E",
"IQTAVRLLLPGELAKHAVSE",
"IQT[-18]AVRLLLPGELAKHAVSE",
"IQTAVRLLLPGELAK[+28]HAVSE",
"IQT[-18]AVR[+14]LLLP[+32]GELAKHAVSE",
"I[+43]QTAVRLLLPGE[+22]",
"I[+57]QT[+80]AVRLLLPGE[+22]LAKHAVSE",
"IQ[+1]T[-18]AVRLLLPGELAKHAVSE",
"IQTAVR[+28]LLLPGELAKHAVSE",
"I[+43]QT[-18]AVR[+16]LLLPGELAKHAVSE",
"I[+43]QTAVRLLLPGELAK[+32]HAVS[-18]E",
"I[+43]Q[+1]TAVRLLLPGE",
"IQTAVRLLLPGE[+37.9]LAKHAVSE",
"IQTAVRLLLPGELAK[+42]HAVSE",
"IQTAVRLLLPGELAK[+32]HAVSE",
"LAK[+14]HAVSE[+57]GTKAVTKYTSSK",
"L[+28]AKHAVSE",
"LAK[+42]HAVSEGTK[+43]AVTKYTSSK",
"LAK[+43]HAVSE",
"L[+43]AK[+43]HAVSE",
"L[+43]AKHAVSE",
"LAK[+42]HAVS[-18]E[+57]GTKAVTKYTSSK",
"LAK[+28]HAVSE",
"L[+43]AKH[+57]AVSE",
"L[+43]AKHAVSE[+22]",
"LAKHAVSEGTK[+28]AVTK[+156.1]YTSSK",
"G[+57]T[+80]K[+114]AVTKYTSSK",
"G[+43]TKAVTK[+43]YTSSK",
"G[+28]TK[+28]AVTKYTSSK",
"G[+57]TK[+42]AVTKYTSSK",
"GTKAVTKYTS[+44]SK",
"GTK[+28]AVTKYTSSK",
"GTK[+43]AVTKYTSSK",
"G[+43]TKAVTKYTSSK",
"G[+28]TK[+16]AVTKYTSSK",
"G[+28]T[-18]K[+28]AVTKYTSSK",
"G[+43]TKAVTK[+16]YTSSK",
"GTK[+43]AVTK[+16]YTSSK",
"GTK[+42]AVTKYTSSK",
"G[+57]T[-18]KAVTKYTSSK",
"G[+43]TK[+43]AVTKYTSSK",
"GTKAVTK[+43]YTSSK",
"GTKAVT[-18]K[+72]Y[-18]TSSK",
"G[+43]TK[+16]AVTKYTSSK",
"GTKAVTK[+42]YTSSK",
"GTKAVTKYTSSK",
"GT[+114]KAVTKYTSSK",
"GTK[+114]AVTKYTSSK",
"GT[-18]K[+114]AVTKYTSSK",
"G[+28]TKAVTKYTSSK",
"GT[-18]K[+72]AVT[-18]KYTSSK",
"G[+57]TKAVTKYTSSK",
"YLT[-18]AEVLELAGNASKD[-1]",
"YLTAEVLELAGNASK[+226.1]D[-1]",
"LAGNASKDLKVK[+72]RITPRH[+57]LQLAIRGDE",
"LKVKRITPRHLQLAIRGDEE",
"LDSLIKATIAGGGVIPHIHK[+14]SLIGKKGQ[+1]QKTV",
"LDSLIKATIAGGGVIPHIHKSLIGKKGQ[+1]Q[+1]KTV",
"LDSLIKATIAGGGVIPHIHKSLIGKKGQQKT[-18]V[+22]",
"LDSLIKATIAGGGVIP[+16]HIHKS[-18]LIGKKGQQKTV",
"LDSLIKATIAGGGVIPHIHKSLIGKKGQQKTV",
"LDSLIKATIAGGGVIPHIHKSLIGK[+28]KGQ[+1]QKTV",
"LDSLIKATIAGGGVIPHIHKSLIGKKGQ[+1]QK[+28]TV",
"LDSLIKATIAGGGVIP[+32]HIHKSLIGKKGQQKTV[+37.9]",
"LDSLIKATIAGGGVIPHIHKSLIGK[+14]KGQ[+1]QKTV",
"L[+43]IVKAVAASKE",
"LIVKAVAASKE[+22]",
"L[+57]IVK[+43]AVAASKE",
"LIVK[+71]AVAASKE",
"L[+43]IVKAVAASKE[+22]",
"L[+57]IVKAVAASK[+43]E",
"L[+43]IVKAVAASK[+43]E",
"L[+28]IVKAVAASKE",
"LIVKAVAASK[+43]E",
"LIVKAVAASKE[+57]",
"LIVK[+43]AVAASK[+43]E",
"L[+43]IVK[+28]AVAASKE",
"L[+43]IVKAVAASKE[+57]",
"L[+28]IVK[+42]AVAASKE",
"L[+43]IVK[+43]AVAASKE",
"LIVK[+32]AVAASKE",
"L[+57]IVKAVAASKE",
"LIVKAVAASKE",
"LIVK[+43]AVAASKE",
"LIVKAVAASK[+156.1]E",
"RSGVSAAALK[+226.1]KALAAGGYD",
"RSGVSAAALKK[+71]ALAAGGYDVD[-1]",
"RSGVSAAALKKALAAGGYD[+53.9]",
"RSGVSAAALKK[+32]ALAAGGY[-18]D",
"RSGVSAAALK[+71]KALAAGGYD[-18]",
"RSGVSAAALKK[+43]ALAAGGYD",
"RSGVSAAALK[+28]KALAAGGYDVD[-1]",
"RSGVSAAALKK[+42]ALAAGGYD[-1]",
"RSGVSAAALKKALAAGGY[-18]D[+22]VD",
"A[+57]SKK[+16]KGKSSTE",
"TYAMYIYKVLKQVHPD",
"AS[-18]R[+28]LAQYNKRSTITSRE",
"ASRLAQY[-18]N[+1]K[+28]RSTITSRE",
"ASRLAQ[+1]YNKRSTITSRE",
"AS[-18]R[+32]LAQYNKRSTITSRE",
"AS[+80]R[+14]LAQYNKRSTITSRE",
"AS[-18]R[+28]LAQYN[+1]KRSTITSRE",
"ASRLAQ[+1]Y[-18]NK[+28]RSTITSRE",
"ASRLAQ[+1]YNKR[+32]STITSRE",
"ASRLAQYNKRSTITSREVQTAVRLLLPGE",
"ASRLAQYNK[+32]R[+1]STITSRE",
"A[+43]S[-18]R[+32]LAQYNKRSTITSRE",
"AS[+44]RLAQYNKRSTITSRE",
"ASRLAQY[-18]NK[+72]RSTITSRE",
"A[+43]SRLAQYNKR[+28]STITSRE",
"ASRLAQYNKR[+1]STITSRE",
"ASRLAQYNKRSTITSRE",
"ASRLAQYNKR[+16]STITSRE",
"AS[-18]R[+28]LAQ[+1]YNKRSTITSRE",
"AS[-18]RLAQY[-18]N[+541.1]KRSTITSRE",
"ASRLAQYNK[+43]RSTIT[-18]SRE",
"A[+43]SRLAQYNKRS[-18]TITSRE",
"ASRLAQYNK[+14]RSTITSRE",
"V[+57]QTAVR[+1]LLLPGELAK[+42]HAVSE",
"V[+57]QTAVRLLLPGELAKH[+57]AVSE",
"V[+28]QTAVRLLLPGE",
"VQTAVR[+14]LLLPGELAKH[+57]AVSE",
"VQ[+1]T[+114]AVR[+28]LLLPGELAKHAVSE",
"VQT[-18]AVR[+32]LLLPGELAKH[+57]AVSE",
"VQTAVR[+14]LLLPGE",
"VQT[-18]AVR[+32]LLLP[+32]GELAKHAVSE",
"V[+57]QTAVRLLLPGE[+22]LAKHAVSE",
"VQTAVR[+14]LLLPGE[+57]LAKHAVSE",
"VQT[-18]AVR[+32]LLLPGELAK[+28]HAVSE",
"VQT[-18]AVR[+32]LLLPGELAKHAVSE",
"VQTAVR[+14]LLLPGELAKHAVSE",
"V[+28]Q[+1]TAVR[+16]LLLPGELAKHAVSE",
"VQ[+1]T[+42]AVR[+14]LLLPGE",
"V[+28]QTAVRLLLPGELAKHAVSE",
"VQTAVRLLLPGELAKHAVSE",
"VQTAVR[+16]LLLPGELAKHAVSE",
"V[+28]QTAVR[+14]LLLPGELAKHAVSE",
"V[+28]QTAVR[+1]LLLP[+16]GELAKHAVSE",
"V[+28]QT[-18]AVRLLLPGELAKHAVSE",
"V[+57]QTAVRLLLPGE",
"V[+57]QTAVRLLLPGELAKHAVSE",
"V[+28]Q[+1]TAVR[+28]LLLPGELAKHAVSE",
"VQT[-18]AVR[+32]LLLPGE[+22]LAKHAVSE",
"V[+43]QTAVR[+14]LLLPGELAKHAVSE",
"V[+43]QTAVR[+16]LLLPGELAKHAVSE",
"V[+43]QT[-18]AVR[+32]LLLPGELAKHAVSE",
"V[+28]QT[-18]AVR[+32]LLLPGELAKHAVSE",
"V[+57]QTAVRLLLPGE[+22]",
"VQ[+1]T[+42]AVR[+28]LLLPGE",
"VQT[+42]AVR[+16]LLLPGE",
"V[+43]Q[+1]TAVR[+1]LLLPGELAKHAVSE",
"V[+57]QT[-18]AVR[+32]LLLPGELAKHAVSE",
"VQ[+1]T[-18]AVR[+28]LLLPGE",
"IQTAVRLLLPAAE[+37.9]",
"IQTAVRLLLP[+32]AAE[+22]",
"IQ[+1]T[+42]AVR[+28]LLLPAAE",
"ETRGVLKVFLE",
"ET[-18]RGVLK[+14]VFLE",
"E[+57]TRGVLKVFLE",
"ET[-18]RGVLKVFLE",
"E[+57]T[-18]RGVLKVFLE",
"ETR[+1]GVLK[+42]VFLE",
"ETRGVLK[+43]VFLE",
"E[+43]TRGVLKVFLE",
"ET[+42]R[+1]GVLKVFLE",
"T[+57]R[+1]GVLKVFLE[-1]",
"TRGVLK[+16]VFLE",
"T[+43]RGVLK[+16]VFLE",
"T[+43]RGVLK[+43]VFLE",
"TR[+1]GVLK[+114]VFLE[+53.9]NVIRDAVTYTE",
"TRGVLKVFLE[+57]",
"TRGVLKVFLE[+37.9]",
"TRGVLK[+71]VFLE",
"TRGVLKVFLE[+22]",
"T[+80]R[+14]GVLKVFLE[+37.9]NVIRDAVTYTE",
"T[+57]RGVLK[+16]VFLE",
"TRGVLK[+32]VFLE",
"TR[+32]GVLKVFLE",
"T[+57]RGVLKVFLE",
"T[+42]R[+1]GVLK[+14]VFLE",
"TRGVLKVFLE",
"T[-18]R[+32]GVLK[+14]VFLE",
"TRGVLK[+28]VFLE",
"TRGVLKVFLE[+53.9]",
"T[-18]R[+14]GVLK[+32]VFLE",
"T[+43]RGVLKVFLE",
"TRGVLK[+43]VFLE",
"T[+28]RGVLKVFLE",
"TR[+1]GVLK[+42]VFLE",
"T[+42]R[+16]GVLKVFLE",
"TR[+16]GVLK[+42]VFLE",
"T[+43]RGVLK[+72]VFLE[+53.9]NVIRDAVTYTE",
"T[+42]R[+1]GVLKVFLE",
"T[+43]RGVLK[+72]VFLE[+37.9]NVIRDAVTYTE",
"T[+57]R[+1]GVLKVFLE",
"T[+43]RGVLKVFLE[+53.9]",
"NVIR[+16]DAVT[-18]YTE",
"NVIRDAVTYTE[+22]",
"NVIR[+16]DAVTY[-18]TE",
"NVIRDAVTYTEHAKRK[+42]TVTAMD",
"NVIRDAVTYTEHAK[+28]RK[+28]TVTAMD",
"NVIRDAVTYTEHAKR[+32]K[+32]TVTAMD",
"NVIRDAVTYTEHAKRK[+42]TVTAMD[-1]",
"NVIRDAVTYTEHAK[+42]RKTVTAMD",
"NVIRDAVTYTEHAKRKT[-18]VT[+80]AMD",
"NVIRDAVTYTEHAKR[+16]K[+32]TVTAMD",
"NVIRDAVTYTE[+37.9]",
"NVIRDAVTYTEHAK[+32]R[+16]KTVTAMD",
"N[+1]VIRDAVT[+42]YTE",
"NVIR[+1]DAVTYTE",
"N[+43]VIRDAVTYTE",
"NVIRD[+57]AVTYTE",
"N[+57]VIRDAVTYTE",
"NVIRDAVTYT[-18]E[+22]",
"N[+43]VIRDAVTYTE[+57]",
"N[+1]VIRDAVTYTE",
"N[+43]VIRDAVTYTE[+53.9]",
"N[+43]VIRDAVTYTE[+37.9]",
"N[+43]VIR[+1]DAVTYTE",
"NVIR[+14]DAVTY[-18]TE",
"N[+43]VIRDAVTYTE[+22]",
"NVIRD[+57]AVTYTE[+22]",
"NVIRDAVTYTE[-1]",
"NVIRDAVTYTEHAK[+32]RKTVTAMD[-1]",
"NVIR[+1]DAVT[+42]YTE",
"NVIR[+1]DAVTYTE[-1]",
"NVIRDAVTY[-18]T[+42]E",
"N[+58]VIRDAVTYTE",
"N[+57]VIR[+1]DAVTYTE",
"NVIRDAVTYTE[+61.9]",
"NVIRDAVT[+42]Y[-18]T[-18]E",
"NVIRDAVTYTE",
"HAKRKTVTAMDVVYSFGG",
"LNKLLGRVTIAQGGVLPNIQAVLLPKK[+156.1]TEKAK[+71]",
"LNKLLGRVTIAQGGVLPNIQAVLLPK[+71]K[+156.1]TEKAK",
"LNKLLGRVTIAQGGVLPNIQAVLLPK[+156.1]K[+72]TEKAK",
"LNKLLGRVT[-18]IAQ[+1]GGVLPNIQAVLLPKKTE",
"VAPAAAPAPATE",
"V[+43]APAAAPAPATE",
"VAPAAAPAPATE[+22]",
"L[+43]IVKAVKE",
"LIVKAVKE",
"L[+57]IVKAVKE",
"LIVK[+14]AVK[+16]E[+57]SKE",
"LIVKAVKESK[+42]E[-1]",
"LIVKAVK[+42]ESKE[-1]",
"RKGLS[+86]LAAIKKD",
"LVARGYDVE",
"L[+57]VARGYDVE",
"L[+43]VARGYDVE",
"ETP[+32]APAPAPAKAAKK[+71]KKTTASKPKKVGPSVGE",
"ETPAPAPAPAK[+43]AAK[+32]KKKTTASKPKKVGPSVGE",
"ETP[+32]APAPAPAK[+72]AAKKKKTTASKPKKVGPSVGE",
"ETPAPAPAP[+16]AK[+43]AAKKKKTTASKPKKVGPSVGE",
"ETPAPAPAPAKAAK[+43]K[+32]KKTTASKPKKVGPSVGE",
"ETPAPAP[+16]APAK[+43]AAKKKKTTASKPKKVGPSVGE",
"ETPAPAPAPAK[+72]AAKKKKTTASKPKKVGPSVGE",
"ETPAPAPAP[+32]AK[+156.1]AAKKKKTTASKPKKVGPSVGE",
"MSEEAPAPAPAPAK[+42]AAKKKTTASKPKKVGPSVGE",
"MSEEAPAPAPAPAKAAKK[+42]KTTASKPKKVGPSVGE",
"MSEEAPAPAPAPAKAAKKKTTASKPKKVGPSVGE",
"E[+226.1]AP[+32]APAPAPAKAAKKKTTASKPKKVGPSVGE",
"E[+226.1]APAPAPAPAK[+72]AAKKKTTASKPKKVGPSVGE",
"E[+61.9]APAPAPAPAKAAKK[+72]KKTTASKPKKVGPSVGE",
"E[+61.9]APAPAPAPAK[+43]AAKKKKTTASKPKKVGPSVGE",
"EAPAPAPAPAKAAKKKKTTASKPKKVGPSVGE",
"APAPAPAPAKAAKKKKTTASKPKKVGPSVGE",
"RS[+80]GVSTAALKKALAAGGYD",
"I[+43]RRYQKSTE",
"I[+28]RRYQKSTE",
"LLIR[+1]K[+16]LPFQRLVRE",
"LLIR[+32]K[+43]LPFQRLVRE",
"LLIRK[+28]LPFQRLVRE",
"LLIRKLP[+16]FQRLVRE",
"LLIR[+16]KLPFQRLVRE",
"LLIRKLP[+32]FQRLVRE",
"LLIR[+32]KLPFQRLVRE",
"L[+28]LIR[+16]KLPFQRLVRE",
"LLIR[+1]K[+14]LPFQRLVRE",
"LLIR[+1]K[+43]LPFQRLVRE",
"L[+57]LIR[+1]KLPFQRLVRE",
"L[+57]LIRKLPFQRLVRE",
"LLIRK[+71]LPFQRLVRE",
"LLIR[+1]K[+71]LPFQRLVRE",
"LLIR[+1]K[+42]LPFQRLVRE",
"L[+43]LIRKLPFQRLVRE",
"L[+43]LIRKLPFQR[+1]LVRE",
"L[+43]LIRKLPFQ[+1]RLVRE",
"L[+28]LIRKLPFQRLVRE",
"LLIRKLPFQ[+1]RLVRE",
"LLIRKLPFQR[+1]LVRE",
"LLIRKLPFQRLVRE",
"L[+28]LIR[+32]K[+14]LPFQRLVRE",
"LLIRK[+43]LPFQRLVRE",
"L[+43]LIRKLP[+32]FQRLVRE",
"L[+43]LIR[+32]KLPFQRLVRE",
"IAQDFKTD",
"IAQ[+1]DFKTD",
"IAQDFK[+43]TDLR[+28]FQSSAVMALQE",
"IAQDFKTDLR[+28]FQSSAVM[+16]ALQE",
"I[+43]AQD[+22]FKTD",
"IAQDFK[+14]TD",
"IAQDFK[+14]TDLRFQSSAVMALQE[+57]",
"IAQDFKTDLR[+14]FQSSAVMALQE[+57]",
"I[+57]AQDFKTD",
"IAQDFK[+43]TDLR[+14]FQSSAVMALQE",
"IAQDFK[+43]TD[+57]LRFQSSAVMALQE",
"IAQDFKTD[+57]LRFQSSAVMALQE",
"I[+43]AQDFKTD",
"IAQDFK[+71]TDLRFQSSAVMALQE",
"I[+43]AQDFKTDLRFQSSAVMALQE[+57]",
"IAQDFK[+43]TDLRFQSSAVMALQE[+57]",
"IAQDFK[+43]TDLRFQSSAVM[+16]ALQE",
"IAQDFK[+156.1]T[+114]DLRFQSSAVMALQE",
"IAQDFKTD[+57]LRFQ[+1]SSAVMALQE",
"IAQDFKTDLRFQSSAVMALQE[+57]",
"IAQDFK[+72]TDLRFQSSAVMALQ[+1]E",
"IAQDFK[+28]TD",
"IAQDFK[+28]TDLRFQSSAVM[+16]ALQE",
"LRFQSSAVMALQE",
"LRFQSSAVM[+16]ALQE",
"L[+43]RFQSSAVM[+16]ALQE",
"L[+57]RFQSSAVM[+16]ALQE",
"LRFQSSAVM[+16]ALQ[+1]E",
"A[+57]YLVGLFE",
"AYLVGLFE[+53.9]",
"AYLVGLFE[+61.9]",
"AYLVGLFE[+22]",
"A[+43]YLVGLFE[+22]",
"AYLVGLFE",
"DTNLC[+57]AIHAKRVTIMPKD",
"MSEEAPAPAPAPAK[+14]ATKKKTTASKPKKVGPSVGE",
"MS[-18]EEAPAPAPAPAK[+28]ATKKKTTASKPKKVGPSVGE",
"MS[-18]EEAPAPAPAPAKATK[+28]KKTTASKPKKVGPSVGE",
"2_MS[-18]EEAPAPAPAPAK[+28]ATKKKTTASKPKKVGPSVGE",
"LNQLLKGVTIAAGGVLPNIHPELLAKKRGAKGKLE",
"LNQLLKGVTIAAGGVLPNIHPE",
"GPSLPKLIVASVTE",
"G[+43]PSLPKLIVASVTE",
"G[+57]PS[+44]LPK[+28]LIVASVTE",
"G[+57]PSLPK[+72]LIVASVTE",
"RKGTSLAAIKKYLTAKNVDVPKAN[+1]KRINTAVAKLVE",
"RKGTSLAAIKKYLTAKNVDVPKANKRIN[+1]TAVAKLVE",
"RKGTSLAAIKKYLTAKNVDVPKANKRINTAVAKLVE",
"RKGTSLAAIKKYLTAKNVDVPKAN[+1]KR[+1]INTAVAKLVE",
"RKGTSLAAIKKYLTAKNVDVPKANKR[+1]IN[+1]TAVAKLVE",
"RKGTSLAAIKKYLTAKNVDVPKANK[+14]RINT[-18]AVAKLVE",
"VP[+32]KANKRINT[+80]AVAKLVE",
"V[+43]APAPAAAPAKPAKKKASKPKKTGPSVSDQ[+1]ILKVVTASKE",
"VAPAPAAAPAKPAKKKASK[+28]PKKTGPSVSDQ[+1]ILKVVTASKE",
"VAPAPAAAPAKPAKKK[+42]ASK[+16]PKKTGPSVSDQILKVVTASKE",
"V[+28]AP[+16]APAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"V[+42]AP[+16]APAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"V[+43]APAP[+16]AAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"V[+57]APAPAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAPAKPAKKK[+43]ASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAP[+16]AK[+28]PAKKKASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAP[+32]AK[+14]PAKKKASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAPAK[+42]PAKKKASKPKKTGPSVSDQ[+1]ILKVVTASKE",
"VAPAPAAAPAKPAKKKASKPKKTGPSVSD",
"V[+43]APAPAAAPAKPAKKKASK[+43]PKKTGPSVSDQILKVVTASKE",
"V[+43]APAPAAAPAKPAKKKASKPKKTGPSVSDQILKVVTASKE",
"VAPAPAAAP[+32]AK[+28]PAKKKASKPKKTGPSVSDQILKVVTASKE",
"QILKVVTASKE",
"Q[+43]ILKVVTASKE",
"Q[-17]ILKVVTASKE",
"Q[+57]ILK[+226.1]VVTASKE",
"Q[+226.1]ILK[+71]VVTASKE",
"Q[+226.1]ILK[+72]VVTASKE",
"RK[+32]GVS[-18]LAALK[+43]KALAAGGYDVE",
"RK[+43]GVSLAALKKALAAGGYD[+53.9]VE",
"R[+43]KGVSLAALKK[+32]ALAAGGYDVE",
"R[+57]K[+43]GVSLAALKKALAAGGYDVE",
"RK[+14]GVSLAALK[+43]KALAAGGYDVE",
"RKGVSLAALK[+32]KALAAGGYDVE",
"R[+57]KGVSLAALKKALAAGGYDVE",
"R[+43]K[+32]GVS[-18]LAALKKALAAGGYDVE",
"R[+14]KGVSLAALK[+43]KALAAGGYDVE",
"R[+43]KGVSLAALKK[+14]ALAAGGYDVE",
"R[+43]KGVSLAALK[+14]KALAAGGYDVE",
"RK[+43]GVSLAALK[+32]KALAAGGYDVE",
"R[+43]KGVSLAALKKALAAGGYDVE[+53.9]",
"RK[+43]GVSLAALKKALAAGGYD[+37.9]VE",
"RKGVSLAALKK[+32]ALAAGGYDVE",
"R[+1]KGVSLAALKKALAAGGYDVE",
"RKGVSLAALK[+114]K[+114]ALAAGGYD",
"RKGVSLAALKKALAAGGYDVE[+22]",
"R[+43]KGVSLAALKKALAAGGYDVE",
"RK[+43]GVSLAALKKALAAGGYDVE",
"R[+1]K[+42]GVSLAALKKALAAGGYDVE",
"RKGVSLAALK[+43]KALAAGGYDVE",
"R[+1]KGVSLAALK[+42]KALAAGGYDVE",
"RKGVSLAALKK[+43]ALAAGGYDVE",
"R[+43]KGVSLAALKK[+43]ALAAGGYDVE",
"R[+1]KGVSLAALKK[+42]ALAAGGYDVE",
"RK[+43]GVSLAALKKALAAGGYDVE[+53.9]",
"RKGVSLAALKKALAAGGYD[+57]VE",
"RKGVSLAALKKALAAGGYD[-18]VE",
"R[+28]KGVSLAALKKALAAGGYDVE",
"R[+1]KGVSLAALK[+43]KALAAGGYDVE",
"RKGVSLAALKKALAAGGYDVE[+37.9]",
"R[+43]KGVSLAALKKALAAGGYDVE[+37.9]",
"RKGVSLAALK[+16]K[+42]ALAAGGYDVE",
"RKGVSLAALKKALAAGGYD[+37.9]VE",
"RKGVSLAALKKALAAGGYDVE[+57]",
"RKGVSLAALKKALAAGGYD[+22]VE",
"R[+43]KGVSLAALKKALAAGGYD[+37.9]VE",
"RKGVSLAALKK[+71]ALAAGGYDVE",
"R[+43]K[+43]GVSLAALKKALAAGGYDVE",
"KN[+1]NARVKIAIKSLVSKGTLVQTKGTGASGSFKLGKKAAE",
"K[+42]NNAR[+1]VKIAIKSLVSKGTLVQTKGTGASGSFKLGKKAAE",
"KNN[+1]ARVKIAIKSLVSKGTLVQTKGTGASGSFKLGKKAAE",
"K[+43]NNARVKIAIKSLVSKGTLVQTKGTGASGSFKLGKKAAE",
"KNNARVK[+43]IAIKSLVSKGTLVQTKGTGASGSFKLGKKAAE",
"KNNAR[+1]VKIAIKSLVSKGTLVQTKGTGASGSFKLGKKAAE",
"KNNAR[+1]VKIAIKS[-18]LVSKGTLVQTKGTGASGSFKLGKKAAE"
)
```

#Sorting Napho Files: 

Gills/Napho/Exp1

```{r}
Gills_Napho_Exp1 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Gills_Napho_Exp1.csv")

Sorted_Gills_Napho_Exp1 <- Gills_Napho_Exp1[match(Target_Napho, Gills_Napho_Exp1$`Peptide Modified Sequence`),]

write_csv(Sorted_Gills_Napho_Exp1, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Gills_Napho_Exp1.csv")
```

Kidney/Napho/Exp1

```{r}
Kidney_Napho_Exp1 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Kidney_Napho_Exp1.csv")

Sorted_Kidney_Napho_Exp1 <- Kidney_Napho_Exp1[match(Target_Napho, Kidney_Napho_Exp1$`Peptide Modified Sequence`),]

write_csv(Sorted_Kidney_Napho_Exp1, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Kidney_Napho_Exp1.csv")
```

Testes/Napho/Exp1

```{r}
Testes_Napho_Exp1 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Testes_Napho_Exp1.csv")

Sorted_Testes_Napho_Exp1 <- Testes_Napho_Exp1[match(Target_Napho, Testes_Napho_Exp1$`Peptide Modified Sequence`),]

write_csv(Sorted_Testes_Napho_Exp1, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Testes_Napho_Exp1.csv")
```


Gills/Napho/Exp2

```{r}
Gills_Napho_Exp2 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Gills_Napho_Exp2.csv")

Sorted_Gills_Napho_Exp2 <- Gills_Napho_Exp2[match(Target_Napho, Gills_Napho_Exp2$`Peptide Modified Sequence`),]

write_csv(Sorted_Gills_Napho_Exp2, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Gills_Napho_Exp2.csv")
```


Kidney/Napho/Exp2

```{r}
Kidney_Napho_Exp2 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Kidney_Napho_Exp2.csv")

Sorted_Kidney_Napho_Exp2 <- Kidney_Napho_Exp2[match(Target_Napho, Kidney_Napho_Exp2$`Peptide Modified Sequence`),]

write_csv(Sorted_Kidney_Napho_Exp2, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Kidney_Napho_Exp2.csv")
```


Testes/Napho/Exp2

```{r}
Testes_Napho_Exp2 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Testes_Napho_Exp2.csv")

Sorted_Testes_Napho_Exp2 <- Testes_Napho_Exp2[match(Target_Napho, Testes_Napho_Exp2$`Peptide Modified Sequence`),]

write_csv(Sorted_Testes_Napho_Exp2, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Testes_Napho_Exp2.csv")
```



## Correcting the order of all Trypsin files

Creating vectors that contain the desired order for each DIA assay library, based on Kidney/Exp1 order:

```{r}

Target_Trypsin <- c(
"G[+56]K[+56]TGGK[+56]AR",
"G[+43]K[+56]TGGK[+56]AR",
"S[+56]S[+114]RAGLQFPVGR",
"S[+114]S[+56]RAGLQFPVGR",
"S[-18]S[+114]RAGLQFPVGR",
"S[+226.1]SR[+1]AGLQFPVGR",
"S[+42]S[+56]RAGLQFPVGR",
"S[+57]S[+56]RAGLQFPVGR",
"SS[+114]R[+14]AGLQFPVGR",
"S[+56]S[+114]R[+1]AGLQFPVGR",
"S[+226.1]S[-18]RAGLQ[+1]FPVGR",
"S[+57]S[+114]R[+42]AGLQFPVGR",
"AGLQFPVGR",
"A[+56]GLQFPVGR",
"A[+43]GLQFPVGR",
"A[+57]GLQFPVGR",
"AGLQ[+1]FPVGR",
"AGLQFPVGR[-1]",
"A[+56]GLQ[+1]FPVGR",
"A[+56]GLQFPVGR[-1]",
"A[+43]GLQ[+1]FPVGR",
"A[+57]GLQ[+1]FPVGR",
"L[+56]LR[+28]K[+28]GNYAER",
"K[+56]GNYAER",
"K[+112.1]GNYAER",
"IIP[+16]RHLQLAVR",
"IIP[+16]R[+1]HLQLAVR",
"HLQLAVR",
"H[+56]LQLAVR",
"H[+43]LQLAVR",
"HLQLAVR[+14]",
"I[+56]AAEASR",
"L[+56]AHYNK[+56]R",
"E[+56]IQTAVR",
"LLLPGELAK[+56]HAVSEGTK[+56]AVTK[+56]YTSSK",
"S[+114]QRAGLQFPVGR",
"S[+56]QR[+42]AGLQFPVGR",
"S[+114]QR[+14]AGLQFPVGR",
"S[+114]QR[+42]AGLQFPVGR",
"S[-18]QR[+32]AGLQFPVGR",
"S[+42]QR[+28]AGLQFPVGR",
"I[+43]HRHLK[+14]S[+56]R",
"ITPR[+32]HLQLAIR",
"ITP[+16]R[+16]HLQLAIR",
"HLQLAIR",
"H[+56]LQLAIR",
"SGVSAAALK[+114]KALAAGGYDVDK[+56]NKAR",
"SGVSAAALK[+56]K[+56]ALAAGGYDVDK[+56]NKAR",
"SGVSAAALK[+56]K[+56]ALAAGGYDVDKNK[+56]AR",
"AMSIMNSFVNDLFER",
"AM[+16]SIMNSFVNDLFER",
"AMS[+56]IMNSFVNDLFER",
"AMSIM[+16]NSFVNDLFER",
"AMSIMN[+1]SFVNDLFER",
"AMSIMNS[+56]FVNDLFER",
"AMSIMNSFVN[+1]DLFER",
"A[+56]M[+16]SIMNSFVNDLFER",
"A[+56]MSIMN[+1]SFVNDLFER",
"A[+57]MSIMN[+1]SFVNDLFER",
"AM[+16]S[+56]IMNSFVNDLFER",
"AM[+16]SIM[+16]NSFVNDLFER",
"AM[+16]SIMN[+1]SFVNDLFER",
"AMSIM[+16]N[+1]SFVNDLFER",
"AMSIM[+16]NSFVN[+1]DLFER",
"A[+56]M[+16]SIM[+16]NSFVNDLFER",
"AM[+16]S[+56]IMNS[-18]FVNDLFER",
"AM[+16]S[+56]IMNS[+42]FVNDLFER",
"AM[+16]S[-18]IMNS[-18]FVNDLFER",
"AMS[+56]IM[+16]NS[-18]FVNDLFER",
"AMS[-18]IM[+16]NS[-18]FVNDLFER",
"AMS[+42]IM[+16]NS[+56]FVNDLFER",
"AGVIFPVGR",
"A[+57]GVIFPVGR",
"V[+56]KVDSQASVTDK[+56]QEER",
"VT[+42]VFPRDIQLAR",
"VTVFPR[+28]DIQLAR",
"VTVFPR[+14]DIQLAR",
"VT[+114]VFPR[+14]DIQLAR",
"VT[-18]VFPR[+28]DIQLAR",
"VT[+80]VFPR[+28]DIQLAR",
"VT[+80]VFPR[+42]DIQLAR",
"VT[+42]VFP[+32]RDIQLAR",
"VT[+42]VFPR[+28]DIQLAR",
"VT[+42]VFPR[+42]DIQLAR",
"VT[+56]VFPR[+28]DIQLAR",
"VTVFP[+32]R[+42]DIQLAR",
"VTVFP[+16]R[+28]DIQLAR",
"VTVFP[+16]R[+14]DIQLAR",
"VT[-18]VFP[+32]R[+28]DIQLAR",
"VT[-18]VFP[+32]R[+14]DIQLAR",
"VT[+56]VFP[+32]R[+28]DIQLAR",
"VT[+56]VFP[+32]R[+14]DIQLAR",
"VT[+56]VFP[+32]R[+32]DIQLAR",
"VT[+56]VFP[+32]R[+16]DIQLAR",
"VT[+56]VFP[+16]R[+28]DIQLAR",
"VT[+56]VFP[+16]R[+14]DIQLAR",
"VT[+56]VFP[+16]R[+32]DIQLAR",
"KVVLDNIQGITKPAIR",
"K[+56]VVLDNIQGITK[+56]PAIR",
"KVVLDN[+1]IQGITK[+56]PAIR",
"K[+14]VVLD[-18]NIQGITK[+56]PAIR",
"R[+28]GGVKRISGLIYEETR",
"R[+71]GGVK[+71]RISGLIYEETR",
"GGVK[+32]RISGLIYEETR",
"G[+43]GVK[+42]RISGLIYEETR",
"G[+57]GVK[+28]RISGLIYEETR",
"GGVK[+71]R[+14]ISGLIYEETR",
"G[+56]GVK[+32]R[+28]ISGLIYEETR",
"GGVK[+71]R[+32]IS[-18]GLIYEETR",
"ISGLIYEETR",
"I[+56]SGLIYEETR",
"I[+43]SGLIYEETR",
"I[+57]SGLIYEETR",
"IS[+56]GLIYEETR",
"IS[+42]GLIYEETR",
"ISGLIYEETR[-1]",
"I[+57]S[-18]GLIYEETR",
"ISGLIY[-18]EETR[+16]",
"ISGLIYEET[-18]R[+14]",
"ISGLIYEET[-18]R[+16]",
"G[+56]VLKVFLENVIR",
"GVLK[+56]VFLENVIR",
"GVLK[+114]VFLENVIR",
"G[+56]VLK[+56]VFLENVIR",
"G[+43]VLK[+56]VFLENVIR",
"G[+43]VLK[+43]VFLENVIR",
"G[+57]VLK[+56]VFLENVIR",
"DAVTYTEHAK[+56]R",
"DAVTYTEHAK[+43]R",
"D[+56]AVTYTEHAK[+56]R",
"D[+43]AVTYTEHAK[+56]R",
"D[+43]AVTYTEHAK[+43]R",
"D[+57]AVTYTEHAK[+56]R",
"D[-18]AVTYTEHAK[+56]R",
"DAVT[-18]YTEHAK[+56]R",
"DAVTYTE[+57]HAK[+56]R",
"D[+56]AVTYTE[+57]HAK[+56]R",
"D[+43]AVT[-18]YTEHAK[+56]R",
"D[+43]AVTYTE[+57]HAK[+56]R",
"K[+42]GLS[+56]LAAIK[+56]KDLVAR",
"GYDVEHNSAHVR",
"G[+56]YDVEHNSAHVR",
"G[+43]YDVEHNSAHVR",
"G[+57]YDVEHNSAHVR",
"GYD[+57]VEHNSAHVR",
"GYDVE[+57]HNSAHVR",
"GYDVEHN[+1]SAHVR",
"GYDVEHNS[+56]AHVR",
"GYDVEHNSAHVR[+1]",
"G[+56]YDVEHN[+1]SAHVR",
"G[+56]YDVEHNS[+56]AHVR",
"G[+56]YDVEHNS[+80]AHVR",
"G[+56]YDVEHNSAHVR[+1]",
"G[+43]YDVEHNS[+56]AHVR",
"G[+57]YDVEHNS[+56]AHVR",
"Q[-17]SIQK[+56]YVR",
"LVAAGTLR",
"L[+56]VAAGTLR",
"L[+43]VAAGTLR",
"H[+56]TKGIGASGSFR",
"HTK[+56]GIGASGSFR",
"H[+56]TK[+56]GIGASGSFR",
"H[+56]TK[+43]GIGASGSFR",
"H[+43]TK[+56]GIGASGSFR",
"H[+57]TK[+56]GIGASGSFR",
"H[+57]TK[+43]GIGASGSFR",
"H[+56]TK[+56]GIGAS[+56]GSFR",
"H[+56]TK[+56]GIGASGS[+56]FR",
"H[+57]T[-18]K[+56]GIGASGSFR",
"HTK[+56]GIGASGS[-18]FR[+14]",
"K[+56]STGGK[+56]APR",
"K[+56]STGGK[+42]APR",
"K[+112.1]STGGK[+56]APR",
"K[+112.1]STGGK[+42]APR",
"K[+57]STGGK[+56]APR",
"K[+57]STGGK[+42]APR",
"K[+99]STGGK[+56]APR",
"K[+56]QLATK[+56]AAR",
"K[+56]QLATK[+42]AAR",
"K[+114]QLATK[+56]AAR",
"K[+114]QLATK[+42]AAR",
"K[+112.1]QLATK[+56]AAR",
"K[+112.1]QLATK[+42]AAR",
"K[+112.1]QLATK[+43]AAR",
"K[+57]QLATK[+56]AAR",
"K[+99]QLATK[+56]AAR",
"K[+99]QLATK[+42]AAR",
"K[+99]QLATK[+43]AAR",
"K[+56]Q[+1]LATK[+56]AAR",
"K[+43]QLAT[+80]K[+56]AAR",
"KSAPAT[+114]GGVKKPHR",
"K[+56]SAPATGGVK[+56]KPHR",
"K[+56]SAPATGGVKK[+56]PHR",
"K[+56]SAPATGGVKK[+28]PHR",
"K[+56]SAPATGGVKKPHR[+28]",
"K[+28]SAPAT[+114]GGVKKPHR",
"K[+28]SAPATGGVK[+114]KPHR",
"K[+28]SAPATGGVKK[+114]PHR",
"K[+14]SAPAT[+114]GGVKKPHR",
"K[+71]SAPATGGVK[+56]KPHR",
"2_K[+71]SAPATGGVK[+56]KPHR",
"K[+57]SAPATGGVK[+56]KPHR",
"K[+57]SAPATGGVKK[+28]PHR",
"K[+70]SAPATGGVK[+56]KPHR",
"K[+70]SAPATGGVK[+114]KPHR",
"K[+70]SAPATGGVK[+28]KPHR",
"KS[+56]APATGGVK[+56]KPHR",
"KS[+56]APATGGVK[+28]KPHR",
"KS[+114]APATGGVKK[+56]PHR",
"KSAPATGGVK[+56]K[+56]PHR",
"KSAPATGGVK[+28]K[+56]PHR",
"K[+56]SAPAT[+114]GGVK[+14]KPHR",
"K[+56]SAPATGGVK[+56]K[+56]PHR",
"K[+112.1]S[+56]APATGGVKK[+56]PHR",
"K[+112.1]SAPATGGVK[+56]K[+56]PHR",
"K[+28]S[+56]APATGGVK[+56]KPHR",
"K[+28]S[+56]APATGGVK[+114]KPHR",
"K[+28]S[+56]APATGGVK[+28]KPHR",
"K[+28]S[+80]APATGGVK[+56]KPHR",
"K[+28]SAPAT[+114]GGVK[+42]KPHR",
"K[+28]SAPAT[-18]GGVK[+114]KPHR",
"K[+28]SAPAT[+80]GGVK[+56]KPHR",
"K[+72]S[-18]APATGGVK[+56]KPHR",
"K[+42]S[+56]APATGGVK[+114]KPHR",
"K[+14]S[+56]APATGGVK[+56]KPHR",
"K[+16]SAP[+32]ATGGVK[+56]KPHR",
"K[+32]S[-18]APAT[+114]GGVKKPHR",
"K[+32]S[-18]APATGGVK[+114]KPHR",
"K[+32]SAP[+32]ATGGVK[+56]KPHR",
"KS[+56]APATGGVK[+56]K[+56]PHR",
"KS[+114]APAT[-18]GGVK[+56]KPHR",
"YRPGTVALR",
"Y[+56]RPGTVALR",
"Y[+43]RPGTVALR",
"Y[+57]RPGTVALR",
"Y[+43]R[+16]PGTVALR",
"Y[-18]R[+42]P[+32]GTVALR",
"Y[+43]RPGTVALREIR",
"R[+56]YQKSTELLIR",
"R[+57]YQKSTELLIR",
"RYQK[+56]STELLIR",
"RYQK[+43]STELLIR",
"RYQKS[+56]TELLIR",
"R[+56]YQK[+56]STELLIR",
"R[+56]YQKS[+56]TELLIR",
"R[+43]YQK[+56]STELLIR",
"R[+56]YQ[+1]K[+42]STELLIR",
"R[+56]YQK[+72]S[-18]TELLIR",
"Y[+56]QKSTELLIR",
"Y[+57]QKSTELLIR",
"YQK[+56]STELLIR",
"YQKS[+56]TELLIR",
"Y[+56]QK[+56]STELLIR",
"Y[+43]QK[+56]STELLIR",
"Y[+57]QK[+56]STELLIR",
"Y[-18]QK[+56]STELLIR",
"YQ[+1]K[+56]STELLIR",
"YQK[+14]S[+80]TELLIR",
"YQK[+14]ST[+80]ELLIR",
"Y[+56]QK[+14]S[+80]TELLIR",
"Y[+56]QK[+14]ST[+80]ELLIR",
"Y[+43]QK[+42]S[+80]TELLIR",
"E[+43]IAQDFKTDLR",
"EIAQD[+57]FKTDLR",
"EIAQDFK[+56]TDLR",
"EIAQDFK[+28]TDLR",
"EIAQDFK[+14]TDLR",
"EIAQDFKT[+56]DLR",
"EIAQDFKTD[+57]LR",
"E[+56]IAQDFK[+56]TDLR",
"E[+56]IAQDFK[+28]TDLR",
"E[+56]IAQDFK[+14]TDLR",
"E[+56]IAQDFKTD[+57]LR",
"E[+43]IAQDFK[+56]TDLR",
"E[+43]IAQDFK[+28]TDLR",
"E[+43]IAQDFK[+14]TDLR",
"E[+43]IAQDFKTD[+57]LR",
"E[+57]IAQDFK[+56]TDLR",
"E[+57]IAQDFK[+28]TDLR",
"E[+57]IAQDFK[+14]TDLR",
"EIAQ[+1]DFK[+56]TDLR",
"EIAQD[-18]FK[+56]TDLR",
"EIAQDFK[+56]TDLR[+14]",
"EIAQDFK[+28]T[+42]DLR",
"EIAQDFK[+42]TDLR[+28]",
"EIAQDFK[+14]T[+80]DLR",
"EIAQDFK[+14]T[+42]DLR",
"EIAQDFK[+14]T[+56]DLR",
"EIAQDFK[+71]TDLR[-1]",
"EIAQDFK[+16]T[+42]DLR",
"EIAQDFK[+42]TDLR[+16]",
"E[+56]IAQ[+1]DFK[+56]TDLR",
"E[+56]IAQD[+57]FK[+14]TDLR",
"E[+56]IAQDFK[+56]TDLR[+14]",
"E[+56]IAQDFK[+42]TDLR[+28]",
"E[+56]IAQDFK[+14]TD[+57]LR",
"E[+56]IAQDFK[+71]TDLR[-1]",
"E[+56]IAQDFKTD[+57]LR[-1]",
"E[+43]IAQ[+1]DFK[+56]TDLR",
"VT[+114]IMPKDIQLAR",
"VTIMPK[+56]DIQLAR",
"VTIMPK[+72]DIQLAR",
"VTIMPK[+43]DIQLAR",
"VTIMPKD[+57]IQLAR",
"V[+56]TIMPK[+56]DIQLAR",
"V[+56]TIMPK[+72]DIQLAR",
"V[+56]TIMPKD[+57]IQLAR",
"V[+43]TIMPK[+56]DIQLAR",
"V[+43]TIMPK[+42]DIQLAR",
"V[+43]TIMPK[+43]DIQLAR",
"V[+43]TIMPKD[+57]IQLAR",
"V[+226.1]TIMPK[+56]DIQLAR",
"V[+57]TIMPK[+56]DIQLAR",
"VT[-18]IMPK[+56]DIQLAR",
"VTIM[+16]PK[+56]DIQLAR",
"VTIM[+16]PKD[+57]IQLAR",
"VTIMP[+32]K[+56]DIQLAR",
"VTIMPK[+56]DIQ[+1]LAR",
"VTIMPK[+56]DIQLAR[+1]",
"V[+56]TIM[+16]PK[+56]DIQLAR",
"V[+56]TIMPK[+56]DIQ[+1]LAR",
"V[+43]TIM[+16]PK[+56]DIQLAR",
"V[+43]TIMP[+32]K[+28]DIQLAR",
"V[+57]TIM[+16]PK[+56]DIQLAR",
"V[+57]TIMP[+32]K[+42]DIQLAR",
"V[+57]TIMP[+32]K[+32]DIQLAR",
"VT[+80]IMP[+32]K[+71]DIQLAR",
"VTIM[+16]PK[+56]DIQ[+1]LAR",
"VTIMP[+32]K[+43]D[-18]IQLAR",
"K[+112.1]GVS[+56]LAALKKALAAGGYDVEK[+56]NNAR",
"K[+112.1]GVSLAALKK[+56]ALAAGGYDVEK[+56]NNAR",
"KGVSLAALK[+56]K[+56]ALAAGGYDVEK[+56]NNAR",
"K[+56]AAAK[+56]SHK[+56]QR",
"K[+112.1]AAAK[+56]SHK[+56]QR",
"K[+112.1]AAAKS[+56]HK[+56]QR",
"K[+112.1]KTGPTVSDLILK[+56]ALSTSTQR",
"KK[+56]TGPTVSDLILK[+56]ALSTSTQR",
"K[+56]K[+56]TGPTVSDLILK[+56]ALSTSTQR",
"K[+112.1]K[+56]TGPTVSDLILK[+56]ALSTSTQR",
"K[+112.1]K[+56]TGPTVSDLILKALS[+56]TSTQR",
"K[+112.1]KTGPTVS[+56]DLILK[+56]ALSTSTQR",
"I[+56]LIAVKR",
"ILIAVK[+56]R",
"I[+56]LIAVK[+56]R",
"I[+43]LIAVK[+56]R"
)

```


#Sorting Trypsin Files: 

Gills/Trypsin/Exp1

```{r}
Gills_Trypsin_Exp1 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Gills_Tryp_Exp1.csv")

Sorted_Gills_Trypsin_Exp1 <- Gills_Trypsin_Exp1[match(Target_Trypsin, Gills_Trypsin_Exp1$`Peptide Modified Sequence`),]

write_csv(Sorted_Gills_Trypsin_Exp1, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Gills_Trypsin_Exp1.csv")
```


Kidney/Trypsin/Exp1

```{r}
Kidney_Trypsin_Exp1 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Kidney_Tryp_Exp1.csv")

Sorted_Kidney_Trypsin_Exp1 <- Kidney_Trypsin_Exp1[match(Target_Trypsin, Kidney_Trypsin_Exp1$`Peptide Modified Sequence`),]

write_csv(Sorted_Kidney_Trypsin_Exp1, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Kidney_Trypsin_Exp1.csv")
```


Testes/Trypsin/Exp1

```{r}
Testes_Trypsin_Exp1 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Testes_Tryp_Exp1.csv")

Sorted_Testes_Trypsin_Exp1 <- Testes_Trypsin_Exp1[match(Target_Trypsin, Testes_Trypsin_Exp1$`Peptide Modified Sequence`),]

write_csv(Sorted_Testes_Trypsin_Exp1, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Testes_Trypsin_Exp1.csv")
```

Gills/Trypsin/Exp2

```{r}
Gills_Trypsin_Exp2 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Gills_Tryp_Exp2.csv")

Sorted_Gills_Trypsin_Exp2 <- Gills_Trypsin_Exp2[match(Target_Trypsin, Gills_Trypsin_Exp2$`Peptide Modified Sequence`),]

write_csv(Sorted_Gills_Trypsin_Exp2, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Gills_Trypsin_Exp2.csv")
```


Kidney/Trypsin/Exp2

```{r}
Kidney_Trypsin_Exp2 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Kidney_Tryp_Exp2.csv")

Sorted_Kidney_Trypsin_Exp2 <- Kidney_Trypsin_Exp2[match(Target_Trypsin, Kidney_Trypsin_Exp2$`Peptide Modified Sequence`),]

write_csv(Sorted_Kidney_Trypsin_Exp2, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Kidney_Trypsin_Exp2.csv")
```


Testes/Trypsin/Exp2

```{r}
Testes_Trypsin_Exp2 <- read_csv("../data/Sorting_DIA_Assay_Libraries/Testes_Tryp_Exp2.csv")

Sorted_Testes_Trypsin_Exp2 <- Testes_Trypsin_Exp2[match(Target_Trypsin, Testes_Trypsin_Exp2$`Peptide Modified Sequence`),]

write_csv(Sorted_Testes_Trypsin_Exp2, file = "../data/Sorting_DIA_Assay_Libraries/Sorted_Testes_Trypsin_Exp2.csv")
```




